---
title: "Summary_exome_analysis"
author: "Swetansu Pattnaik"
date: "26/09/2019"
output: html_document
---

```{r setup, include=FALSE}
.libPaths(c( "/home/shu/R/x86_64-redhat-linux-gnu-library/3.4", .libPaths() ) )
knitr::opts_chunk$set(echo = TRUE)
```

##Meta analysis of custom geneset

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggrepel)
library(knitr)
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)
library(topGO)
```

```{r echo=FALSE}
##qqplot function SKAT output
gg_qqplot_genes <- function(data, ci = 0.95, genes, SKAT = NULL) {
  
  if(is.null(SKAT)){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol)
    ps <- data$pval_SKATO
  }
  else if(SKAT == "pval_SKATbin"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol)
    ps <- data$pval_SKATbin
  }
  else if(SKAT == "pval_SKAT"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol)
    ps <- data$pval_SKAT
  }
  # all_genes <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
  n  <- length(ps)
  df <- data.frame(
    observed = -log10(sort(ps)),
    expected = -log10(ppoints(n)),
    #expected = -log10(sort(pe)),
    clower   = -log10(qbeta(p = (1 - ci) / 2, shape1 = 1:n, shape2 = n:1)),
    cupper   = -log10(qbeta(p = (1 + ci) / 2, shape1 = 1:n, shape2 = n:1)),
    gene_ID  = gene_ID
  )
  log10Pe <- expression(paste("Expected -log"[10], plain(P)))
  log10Po <- expression(paste("Observed -log"[10], plain(P)))
  
  genes_all <- c(genes, gene_top)
  df <- mutate(df, sel=ifelse(df$gene_ID %in% genes_all, 1, 0))
  ptest = ggplot(df, aes(expected, observed)) +
    geom_point(aes(col=as.factor(sel))) +
    scale_color_manual(values=c( "black", "red"))
  ptest = ptest + geom_text_repel(data=filter(df, sel > 0), aes(label=gene_ID), colour = "red", size = 3.5,
                                  box.padding = unit(0.35, "lines"),
                                  point.padding = unit(0.3, "lines"))
  ptest + geom_abline(intercept = 0, slope = 1, alpha = 0.5) +
    geom_line(aes(expected, cupper), linetype = 2) +
    geom_line(aes(expected, clower), linetype = 2) +
    xlab(log10Pe) +
    ylab(log10Po) + theme(legend.position="none")
}

source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")

```

**Filter Thresholds** <br />
1. VAF >= 0.25 <br />
2. intra cohort_MAF filter <= 3/(2*Number in cohort) <br />
3. gnomad_AF_NFE <= 0.005 <br />

**Scoring/Weighting** <br />
EigenPhred scale scoring was introduced manually for the following variants:<br />
C3 = EigenPhredscore <br />
C4 = 45 <br />
ClinVar (*Pathogenic/likely Pathogenic*) C5 = 45 <br />
C3/C4 Variants in the last 5 percent of the C-terminal region of the protein = assigned score/2 <br />


```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}

Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Exome_skat_wsing_load123_noCH_C5eqC4_nonmds_gt_isksrisc_sept05_rect_ASP_cmaf.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
#Exome_pc123_srt_SKATO1 <- lapply(df_skat, function(x) x[order(x$pval_SKATO, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})

SKAT_plots_eigen <- lapply(Exome_pc123_srt_SKAT, function(x)gg_qqplot_genes(data = x, ci = 0.95, genes = x[,1], SKAT = "pval_SKATbin"))
main_lab <- c("No Adjustment", "PC123", "Gender", "Gender_PC123")
names(SKAT_plots_eigen) <- main_lab
SKAT_plots_eigen <- lapply(names(SKAT_plots_eigen), function(x) SKAT_plots_eigen[[x]] + ggtitle(x) + theme(plot.title = element_text(size = 8, face = "bold")))
multiplot(plotlist = SKAT_plots_eigen, cols = 2)

```


```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Exome_skat_wsing_load123_noCH_C5eqC4_nonmds_gt_isksrisc_sept05_rect_ASP_cmaf.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})
Exome_pc123_srt_SKAT_case_enr_nCH <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Exome_pc123_srt_SKAT_case_enr_nCH_iskrisc_05Sept_rect_ASP_cmaf.rds")
##Add p-value
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- Map(cbind.data.frame, Exome_pc123_srt_SKAT_case_enr_nCH, Exome_pc123_srt_SKAT)

##Remove genes that have SKATbin_pval >= 0.1, this selects only significant genes for the PPI enrichment
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
  x[x$pval_SKATbin < 0.1 & x$wt_diff > 0,])

##Better option for Enriched list: sort by -log(p_val) * weight difference ; appropriately factors influence of variant on ISKS phenotype

Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, 
                                                  function(x) cbind.data.frame(x, "rank_score" = -log10(x[,13]) * x[,6]))
                                                    
Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_ranked, function(x)
  x[order(x[,16], decreasing = T),])

##get variant tab
pc123_gender_tab_top1000 <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]]
fil_tab_noCH <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/Exome_filt3_nCH_C5eqC4_nonmds_iskrisc_05Sept_rect_ASP.rds")
pc123_gender_tab_top1000_VAR <- fil_tab_noCH[fil_tab_noCH$gene_symbol %in% pc123_gender_tab_top1000$gene & fil_tab_noCH$comb_score >= 5,]
pc123_gender_tab_top1000_VAR$gene_Pval <- pc123_gender_tab_top1000[match(pc123_gender_tab_top1000_VAR$gene_symbol, pc123_gender_tab_top1000$gene),13]
#head(pc123_gender_tab_top1000_VAR[,c(1:6,8:9,11,15,17:18,20,23:25,30,53,57,59:68,72,119:121)])
pc123_gender_tab_top1000_VAR <- pc123_gender_tab_top1000_VAR[,c(1:6,8:9,11,15,17:18,20,23:25,30,53,57,59:68,72,125:132)]
pc123_gender_tab_top1000_VAR <- unique(pc123_gender_tab_top1000_VAR)
write.table(pc123_gender_tab_top1000_VAR, "/home/shu/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Exome_Enriched_pc_gender_controlled_top_geneVARIANTS_sep05_ASP_cmaf.tsv",
            sep = "\t", row.names = F, quote = F)


```


##Use PPI approach to derive differential enrichment of mutated interactomes in ISKS and RISC(15) combined.
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
##get graph degree from the genes in the top 1000 enriched list
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)


get_topSKAT_degree <- function(enr_df){

skat_genes_top100 <- as.character(enr_df[,3])

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)

can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% skat_genes_top100 
                               & as.character(can_net1$to) %in% skat_genes_top100, ])
uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)



ret_df <- as.data.frame(igraph::degree(uniongraph))
ret_df$gene <- rownames(ret_df)
colnames(ret_df)[1] <- c("degree")

l1 <- lapply(ret_df[,2], function(x)as_ids(adjacent_vertices(uniongraph, v = x)[[1]]))
l2 <- lapply(l1, function(x)paste(x, sep=",", collapse=","))
ret_df$interactors <- unlist(l2)

return(ret_df)
}


##Fisher exact test for enrichment of subgraph related to each protein
#gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]][,1:1000]
gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]]

df_degree <- get_topSKAT_degree(gender_PC123_cont_df)
gender_PC123_cont_df$degree <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 1]
gender_PC123_cont_df$int <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 3]
gender_PC123_cont_df$degree <- ifelse(is.na(gender_PC123_cont_df$degree), 0, gender_PC123_cont_df$degree)
gender_PC123_cont_df$rank_PPI <- gender_PC123_cont_df$rank_score * log(gender_PC123_cont_df$degree + 2)
gender_PC123_cont_df <- gender_PC123_cont_df[order(gender_PC123_cont_df$rank_PPI, decreasing = T),]
###latest fisher test based on degrees in biogrid versus enriched graphs

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
top_genes_enr <- as.character(gender_PC123_cont_df$gene)
fisher_fun_new <- function(gene_sym, top_genes){
  
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes 
                               & as.character(can_net1$to) %in% top_genes, ])
uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)

##degree biogrid
deg_biog <- igraph::degree(can_net_graph1)[which(names(igraph::degree(can_net_graph1)) %in% gene_sym)]
deg_union <- igraph::degree(uniongraph)[which(names(igraph::degree(uniongraph)) %in% gene_sym)]
#tot_biog <- igraph::vcount(can_net_graph1) ##should be edge count not vertex count
#tot_union <- igraph::vcount(uniongraph)
tot_biog <- igraph::ecount(can_net_graph1) 
tot_union <- igraph::ecount(uniongraph)

##test
inp <- c(deg_union, deg_biog, tot_union, tot_biog)
   mgrb_tsg <- matrix(inp ,nrow = 2, ncol = 2)
   colnames(mgrb_tsg) <- c("deg_enr", "deg_bio")
   rownames(mgrb_tsg) <- c("Enriched", "Biog")
   #ft <- fisher.test(mgrb_tsg, alternative = "greater")
   ft <- fisher.test(mgrb_tsg)
   ft_df <- cbind.data.frame("gene" =  gene_sym, "PPI_p_val_wt" = ft$p.value,
                             "CI_lower" = ft$conf.int[1],
                             "CI_upper" = ft$conf.int[2],
                             "OR" = ft$estimate)
  
   return(ft_df)
}
##run fisher test
test_fis <- list()
for(i in 1:length(top_genes_enr)){
test_fis[[i]] <- fisher_fun_new(top_genes_enr[i], top_genes_enr)
}
fisher_res <- do.call("rbind.data.frame",test_fis)

ppi_res_fil_final <- cbind.data.frame(gender_PC123_cont_df, fisher_res)

```

##Cliques in the enriched set of genes
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
######Cliques in uniongraph (enriched cliques from SKAT)
top_genes <- as.character(gender_PC123_cont_df$gene)
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes 
                               & as.character(can_net1$to) %in% top_genes, ])

uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)

te1 <- cliques(uniongraph, min=4)
cpx <- names(unlist(te1))
cpx_np_all <- unique(can_net1[as.character(can_net1$from) %in% cpx 
                               & as.character(can_net1$to) %in% cpx, ])
cpx_graph <- igraph::graph.data.frame(cpx_np_all, directed = F)

net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
net_new_t_list <- network(net_mat_t_list, directed = FALSE)
network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
gnet <- ggnet2(net_new_t_list, alpha = 0.75, edge.alpha = 0.5, label = TRUE, label.size = 3,  mode = "kamadakawai") + theme(legend.position = "bottom") + theme(legend.title = element_blank())
  
  gnet

```

##Volcano plot for enriched and protective variants

```{r}

##change input as per requirement
var_all_45 <- read.delim("/home/shu/RVAS/shard_sub_tier3/DT_sheet/Enriched_pc_gender_controlled_all_genes_C5eqC4_noNAs_auto_45.tsv", sep = "\t", header = T)

results = mutate(var_all_45, sig=ifelse(var_all_45$wt_diff  <= -100 | var_all_45$wt_diff >= 100, "Sig", "Not Sig"))

results$nom <- ifelse(results$pval_SKATbin < 0.1 & results$sig == "Sig", "high", "low")

results$log_wt_diff <- ifelse(results$wt_diff > 0, log(results$wt_diff), -log(abs(results$wt_diff)))

p = ggplot(results, aes(log_wt_diff, -log10(pval_SKATbin))) +
  geom_point(aes(col=nom)) + scale_color_manual(values=c("red", "black"))

p + geom_text_repel(data=filter(results, nom == "high"), aes(label=gene)) + theme(legend.position = "none")

```

##Weighted gene set enrichment
##https://cran.r-project.org/web/packages/enrichR/vignettes/enrichR.html
##install from github
```{r}
library(enrichR)
# dbs <- listEnrichrDbs()
# if (is.null(dbs)) websiteLive <- FALSE
# if (websiteLive) head(dbs)

#dbs <- listEnrichrDbs()

dbs <- c("GO_Molecular_Function_2015", "GO_Cellular_Component_2015", "GO_Biological_Process_2015")
#if (websiteLive) enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
#enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
##loop over the interactors of each protein and report the top pathway and p-value

#gender_PC123_cont_df from line 285
enrichr_fun <- function(gene_sym, fil_graph){
  enrichr_df <- list()
  for(i in 1:length(gene_sym)){
    print(i)
  fil_genes <- fil_graph[grep(paste("^", as.character(gene_sym[i]), "$", sep = ""), fil_graph$gene),]
  if(fil_genes$degree == 0){ 
    enrichr_df[[i]] <- NULL 
    }
  else{
prot <- c(as.character(gene_sym[i]), unlist(strsplit(fil_genes$int, split = ",")))
dbs <- c("GO_Molecular_Function_2015", "GO_Cellular_Component_2015", "GO_Biological_Process_2015")
enriched <- enrichr(prot, dbs)
print(length(enriched))
   enrichr_df[[i]] <- cbind.data.frame("gene_hub" =  gene_sym[i], "GO_MF" = enriched[[1]]$Term[1],
                                       "GO_MF_p_val" = enriched[[1]]$P.value[1],
                                       "GO_CC" = enriched[[2]]$Term[1],
                                       "GO_CC_p_val" = enriched[[2]]$P.value[1],
                                       "GO_BP" = enriched[[3]]$Term[1],
                                       "GO_BP_p_val" = enriched[[3]]$P.value[1])
  
  }
  
  }
  return(enrichr_df)
}

gender_PC123_cont_df <- gender_PC123_cont_df[!is.na(gender_PC123_cont_df$gene),]
goNet_enrich <- enrichr_fun(gender_PC123_cont_df$gene, gender_PC123_cont_df)
goNet_enrich_res <- do.call("rbind.data.frame",goNet_enrich)
saveRDS(goNet_enrich_res, file = "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/goNet_enrich_res_sep05_rect_ASP_025pval.rds", compress = T)

#goNet_enrich_res <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/goNet_enrich_res_sep05.rds")


ppi_res_fil_final <- ppi_res_fil_final[!is.na(ppi_res_fil_final$gene),]
fil_graph_final_comb_GO <- ppi_res_fil_final

#fil_graph_final_comb_GO <- cbind.data.frame(fil_graph_final, goNet_enrich_res)
fil_graph_final_comb_GO[,c(25:30)] <- goNet_enrich_res[match(fil_graph_final_comb_GO$gene, goNet_enrich_res$gene_hub),c(2:7)]
write.table(fil_graph_final_comb_GO[,c(1:10,13:14,16:19,21,24:30)], 
file = "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/Sep05_rect_ASP_graph_final_PPI_comb_GO.tsv", sep = "\t", row.names = F, quote = F)

```


##GO meta analysis
```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")

CC_terms <- fil_graph_final_comb_GO$GO_CC
CC_terms <- gsub(" \\(GO*.*$","", CC_terms)
CC_terms <- CC_terms[!is.na(CC_terms)]
CC_terms_df <- as.data.frame(table(CC_terms))
CC_terms_df <- CC_terms_df[order(CC_terms_df$Freq, decreasing = T),]
CC_terms_df$CC_terms <- gsub(" ", "_", CC_terms_df$CC_terms)
CC_terms_df_10 <- CC_terms_df[1:10,]
samp_ord <- CC_terms_df_10$CC_terms
CC_terms_df_10$CC_terms <- factor(CC_terms_df_10$CC_terms,levels=samp_ord,ordered=TRUE)

#ggplot(CC_terms_df[1:10,], aes(x=as.factor(CC_terms), y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_flip() + scale_y_discrete(limits = rev(levels(CC_terms_df$CC_terms)))

ggplot(CC_terms_df_10, aes(x=as.factor(CC_terms), y = Freq)) + geom_bar(stat="identity") + coord_flip() + scale_x_discrete(limits = rev(levels(CC_terms_df_10$CC_terms))) + xlab("")

##combine p-values of top 10 concepts
# b1 <- fil_graph_final_comb_GO[fil_graph_final_comb_GO$GO_CC %in% "nuclear telomere cap complex",c(3,21:22)]
# library(metaseqR)
# b1_combp <- combine.minp(b1[,3])

BP_terms <- fil_graph_final_comb_GO$GO_BP
BP_terms <- gsub(" \\(GO*.*$","", BP_terms)
BP_terms <- BP_terms[!is.na(BP_terms)]
BP_terms_df <- as.data.frame(table(BP_terms))
BP_terms_df <- BP_terms_df[order(BP_terms_df$Freq, decreasing = T),]
BP_terms_df$BP_terms <- gsub(" ", "_", BP_terms_df$BP_terms)
BP_terms_df_10 <- BP_terms_df[1:10,]
samp_ord <- BP_terms_df_10$BP_terms
BP_terms_df_10$BP_terms <- factor(BP_terms_df_10$BP_terms,levels=samp_ord,ordered=TRUE)

#ggplot(BP_terms_df[1:10,], aes(x=as.factor(BP_terms), y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_flip() + scale_y_discrete(limits = rev(levels(BP_terms_df$BP_terms)))

ggplot(BP_terms_df_10, aes(x=as.factor(BP_terms), y = Freq)) + geom_bar(stat="identity") + coord_flip() + scale_x_discrete(limits = rev(levels(BP_terms_df_10$BP_terms))) + xlab("")


MF_terms <- fil_graph_final_comb_GO$GO_MF
MF_terms <- gsub(" \\(GO*.*$","", MF_terms)
MF_terms <- MF_terms[!is.na(MF_terms)]
MF_terms_df <- as.data.frame(table(MF_terms))
MF_terms_df <- MF_terms_df[order(MF_terms_df$Freq, decreasing = T),]
MF_terms_df$MF_terms <- gsub(" ", "_", MF_terms_df$MF_terms)
MF_terms_df_10 <- MF_terms_df[1:10,]
samp_ord <- MF_terms_df_10$MF_terms
MF_terms_df_10$MF_terms <- factor(MF_terms_df_10$MF_terms,levels=samp_ord,ordered=TRUE)

#ggplot(MF_terms_df[1:10,], aes(x=as.factor(MF_terms), y = Freq)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_flip() + scale_y_discrete(limits = rev(levels(MF_terms_df$MF_terms)))

ggplot(MF_terms_df_10, aes(x=as.factor(MF_terms), y = Freq)) + geom_bar(stat="identity") + coord_flip() + scale_x_discrete(limits = rev(levels(MF_terms_df_10$MF_terms))) + xlab("")


###Venn diagram
fil_graph_final_comb_GO$GO_BP <- gsub(" \\(GO*.*$","", fil_graph_final_comb_GO$GO_BP)
fil_graph_final_comb_GO$GO_MF <- gsub(" \\(GO*.*$","", fil_graph_final_comb_GO$GO_MF)
fil_graph_final_comb_GO$GO_CC <- gsub(" \\(GO*.*$","", fil_graph_final_comb_GO$GO_CC)

b1_cc <- fil_graph_final_comb_GO[fil_graph_final_comb_GO$GO_CC %in% "nuclear telomere cap complex",c(3,19:24)]
b1_bp <- fil_graph_final_comb_GO[fil_graph_final_comb_GO$GO_BP %in% "regulation of telomere maintenance via telomerase",c(3,19:24)]
b1_mf <- fil_graph_final_comb_GO[fil_graph_final_comb_GO$GO_MF %in% "telomeric DNA binding",c(3,19:24)]

library(VennDiagram)
gene_ov <- list(CC=b1_cc[,1] , BP=b1_bp[,1] , MF=b1_mf[,1])
v0 <- venn.diagram( gene_ov, filename=NULL, 
                    fill = c("red", "blue", "green"),
                    alpha = 0.50,
                    col = "transparent")
grid.draw(v0)
overlaps <- calculate.overlap(gene_ov)

# extract indexes of overlaps from list names
indx <- as.numeric(substr(names(overlaps),2,2))

for (i in 1:length(overlaps)){
  v0[[6 + indx[i] ]]$label <- paste(overlaps[[i]], collapse = "\n") 
}
grid.newpage()
grid.draw(v0)
```



