---
title: "Manuscript_figures_all"
author: "Swetansu Pattnaik"
date: "13/10/2020"
output: html_document
---
```{r setup, include=FALSE}
.libPaths(c( "/home/shu/R/x86_64-redhat-linux-gnu-library/3.4", .libPaths() ) )
`%nin%` = Negate(`%in%`)
knitr::opts_chunk$set(echo = TRUE)
```

##gene complex comparisons, please refer master script(gene_cmx_OR_AR_AD.R) at Aug31_freeze
##generate tables
```{r echo=FALSE, warning = FALSE}
Shelterin <- c("POT1", "TINF2", "TERF1", "TERF2", "TERF2IP", "SMARCAL1", "STAG3", "TIMELESS")

Glutamate_NMDA <- c("DLG1", "GRIN2A", "GRIA1", "CAM2KB", "CAM2KD")

ZBTB16_complex <- c("ZBTB16", "ATG7", "ASB10", "ASB8", "FBXO7")

CEP_HAUS_core <- c("CEP63", "CEP72", "HAUS4", "HAUS5", "MZT1", "SSNA1")
CEP_HAUS_extn1 <- c("CEP63", "CEP72", "HAUS4", "HAUS5", "MZT1", "SSNA1", "CEP57", "PCM1")
ppi_res_fil_final <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/ppi_res_fil_final_SKATbin_Aug31.tsv", sep = "\t", header = T)
CEP_interactors <- as.character(ppi_res_fil_final[ppi_res_fil_final$gene %in% CEP_HAUS_core,]$int)
CEP_interactors1 <- unique(unlist(lapply(CEP_interactors, function(x) strsplit(x, ","))))
CEP_HAUS_SKATint_complex <- CEP_interactors1

##CEP_HAUS_Biogrid_complex

library(igraph)
can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% CEP_HAUS_core
| as.character(can_net1$to) %in% CEP_HAUS_core, ])
CEP_HAUS_Biogrid_complex <- unique(c(prot_np_all$from, prot_np_all$to))

CENP_complex <- c("CENPC", "CENPF", "BUB1", "BUB1B", "AURKB", "RANGAP1", "RACGAP1", "MAD2L2")

TCP1_complex <- c("TCP1", "CCT2", "CCT6A")

PRPF4_complex <- c("PRPF4", "DHX9", "DHX16", "SF3A1", "CPSF3", "PPIL3")

Sarcoma_genes <- c("TP53", "SDHA", "SDHB", "SDHD")

TP53_control <- c("TP53") #positive control

MPNST_pos <- c("NF1", "LZTR1", "SDHA", "SDHB", "SDHD")

#Breast_cancer_genes <- c("BRCA1", "BRCA2", "PALB2", "RAD51C", "CDH1")
Breast_cancer_genes <- c("BRCA1", "BRCA2", "PALB2")
#"RAD51C", "RAD51D"
library(readxl)
Centrosome_genes <- read_excel("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/PID/Centrosome maturation.xlsx",
                               sheet = 1)
Centrosome_genes <- as.data.frame(Centrosome_genes)
Centrosome_genes <- Centrosome_genes[Centrosome_genes$MoleculeType %nin% "Chemical Compounds",]

Centrosome_genes <- Centrosome_genes[,4]

mito_cell_cycle <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/PID/Mitotic_cell_cycle_genes_HSA_69278.txt", header = T, stringsAsFactors = F)
mito_HSA_69278 <- unique(as.character(mito_cell_cycle$X))

##mitotic check point genes (GO term)
mito_chk_point = read.table("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/git_proj_rvas/Comb_set_round2/ISKS_MGRB_2020/ISKS_AR_AD/mitotic_checkpoint/mitocheck_point.txt",
                            sep = "", header = F, skip = 1, stringsAsFactors = F)
mito_chk_point <- as.character(mito_chk_point$V1)

##mito overlap
mito_43_overlap <- mito_chk_point[mito_chk_point %in% mito_HSA_69278]

#Centriole replication (GO Term)
cent_rep <- read_excel("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/PID/centriole_replication_genes_GO.xlsx",
                       sheet = 1)
cent_rep <- as.data.frame(cent_rep)
cent_rep_genes <- toupper(unique(cent_rep$Symbol)) #40 genes

cpx_genes <- unique(c(Shelterin, Glutamate_NMDA, ZBTB16_complex, CEP_HAUS_core, CEP_HAUS_extn1, CEP_HAUS_SKATint_complex, 
                      CEP_HAUS_Biogrid_complex, CENP_complex, TCP1_complex,PRPF4_complex, Breast_cancer_genes, Sarcoma_genes, 
                      Centrosome_genes, mito_HSA_69278, mito_chk_point, mito_43_overlap, cent_rep_genes, TP53_control, MPNST_pos))

cpx_list <- list(Shelterin, Glutamate_NMDA, ZBTB16_complex, CEP_HAUS_core, CEP_HAUS_extn1, CEP_HAUS_SKATint_complex, 
                 CEP_HAUS_Biogrid_complex, CENP_complex, TCP1_complex,PRPF4_complex, Breast_cancer_genes, Sarcoma_genes, 
                 Centrosome_genes, mito_HSA_69278, mito_chk_point, mito_43_overlap, cent_rep_genes, TP53_control, MPNST_pos)
names(cpx_list) <- c("Shelterin geneset", "Glutamate_NMDA", "ZBTB16_complex", "Centrosome geneset", "CEP_HAUS_extn1", 
                     "CEP_HAUS_SKAT", "CEP_HAUS_Biogrid", "CENP_complex", "TCP1_complex", "PRPF4_complex", "BRCA geneset", 
                     "Sarcoma geneset", "Centrosome_genes", "mito_HSA_69278", "mito_chk_GO", "mito_43", "cent_rep_genes",
                     "TP53", "NF1 geneset")


##Odds ratio using fisher's exact test(use ppi_final_res... file for fisher's test)

isks_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/Exome_para_tab_ISKS_MGRB_C345_Aug31.rds")
isks_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Exome_para_tab_ISKS_MGRB_minusC3_Aug31.rds")

##Epithelial data
epit_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_MGRB_EPIT_2020.rds")
epit_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_MGRB_EPIT_2020_minusC3.rds")

##Epithelial data (minus melanoma)
nmela_epit_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_EPIT_nmela_2020.rds")
nmela_epit_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_EPIT_nmela_2020_noC3.rds")

##Epithelial data (melanoma)
mela_epit_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_EPIT_mela_2020.rds")
mela_epit_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT_AR_AD/SKAT/Exome_para_EPIT_mela_2020_noC3.rds")


##ISKS_complex vs MGRB
isks_complex_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Complex/Exome_para_ISKS_Complex_Aug31.rds")
isks_complex_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Complex/Exome_para_ISKS_Complex_minusC3_Aug31.rds")

##ISKS_TAS vs MGRB
isks_tas_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/TAS/Exome_para_ISKS_TAS_Aug31.rds")
isks_tas_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/TAS/Exome_para_ISKS_TAS_minusC3_Aug31.rds")
##ISKS_SIMPLE vs MGRB
isks_simple_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Simple/Exome_para_ISKS_SIMPLE_2020_Aug31.rds")
isks_simple_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Simple/Exome_para_ISKS_SIMPLE_2020_minusC3_Aug31.rds")

##ISKS_MPNST vs MGRB
isks_mpnst_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/MPNST/Exome_para_ISKS_MPNST_sep30.rds")
isks_mpnst_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/MPNST/Exome_para_ISKS_MPNST_sep30_noC3.rds")


##Combined Sarcoma replication set
sarc_comb_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/Exome_para_CombSarc_Aug31_sep19.rds")
sarc_comb_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/Exome_para_CombSarc_minusC3Aug31_sep19.rds")

########

cpx_OR_fisher <- function(ppi_res,case_coh_size, cont_coh_size, coh){
  ft_df <- list()
  for(i in 1:length(cpx_list)){
    ppi_res_tab <- ppi_res[ppi_res$gene %in% cpx_list[[i]],]
   # ppi_res_tab[,2] <- ifelse(ppi_res_tab[,2] == 0, 1, ppi_res_tab[,2])
    inp <- c(sum(ppi_res_tab[,1]), case_coh_size - sum(ppi_res_tab[,1]) , 
             sum(ppi_res_tab[,2]), cont_coh_size - sum(ppi_res_tab[,2]))
    sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
    colnames(sim_mat) <- c("case", "cont")
    rownames(sim_mat) <- c("hits", "no_hits")
    #ft <- fisher.test(sim_mat, alternative = "greater")
    #ft <- fisher.test(sim_mat)
    ft <- fisher.test(sim_mat, conf.int = T, conf.level = 0.95)
    ft_df[[i]] <- cbind.data.frame("gene" = names(cpx_list)[i] ,"Cases" = sum(ppi_res_tab[,1]),
                                   "Controls" = sum(ppi_res_tab[,2]),
                                   "Fish_pval" = ft$p.value,"CI_lower" = ft$conf.int[1],
                                   "CI_upper" = ft$conf.int[2],
                                   "OR_Fish" = ft$estimate, "case_coh_size" = case_coh_size,
                                     "Coh" = coh)
  }
  return(ft_df)
}
##removed 7 oesphageal samples (Sep30)
cpx_ISKS_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes, 1644, 3205, "ISKSvsMGRB"))
cpx_ISKS_complex_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_complex_mgrb_genes, 837, 3205, "COMPLEXvsMGRB"))
cpx_ISKS_tas_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_tas_mgrb_genes, 362, 3205, "TASvsMGRB"))
cpx_ISKS_simple_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_simple_mgrb_genes, 371, 3205, "SIMPLEvsMGRB"))
cpx_ISKS_mpnst_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mpnst_mgrb_genes, 157, 3205, "MPNSTvsMGRB"))
cpx_EPIT_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(epit_mgrb_genes, 835, 3205, "EPITvsMGRB"))
#cpx_NMELA_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(nmela_epit_mgrb_genes, 660, 3205, "NMELAvsMGRB"))
#cpx_MELA_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(mela_epit_mgrb_genes, 175, 3205, "MELAvsMGRB"))
#Nov2.2020
cpx_NMELA_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(nmela_epit_mgrb_genes, 632, 3205, "NMELAvsMGRB"))
cpx_MELA_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(mela_epit_mgrb_genes, 203, 3205, "MELAvsMGRB"))
#cpx_CAIRN_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(cairns_mgrb_genes, 413, 3205, "CAIRNvsMGRB"))
cpx_REPSET_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(sarc_comb_mgrb_genes, 563, 3205, "REPvsMGRB"))
df_comb_rnd2 <- rbind.data.frame(cpx_ISKS_OR_df, cpx_ISKS_complex_OR_df, cpx_ISKS_tas_OR_df, 
                                 cpx_ISKS_simple_OR_df, cpx_ISKS_mpnst_OR_df, 
                                 cpx_EPIT_OR_df,cpx_NMELA_OR_df,
                                 cpx_MELA_OR_df, cpx_REPSET_OR_df)
df_comb_rnd2$Coh <- as.factor(gsub("vsMGRB", "", df_comb_rnd2$Coh))
df_comb_rnd2_filt <- df_comb_rnd2[df_comb_rnd2$Fish_pval < 0.05, ]

##for heatmap
##C345 subsetted geneset and cohorts 
df_comb_rnd2_sub <- df_comb_rnd2[df_comb_rnd2$Coh %nin% c("TAS", "SIMPLE", "EPIT", "REP") &
                               df_comb_rnd2$gene %in% c("Shelterin geneset", "Centrosome geneset", "BRCA geneset", 
                                                        "TP53", "NF1 geneset"),]
df_comb_rnd2_sub$Coh <- droplevels(df_comb_rnd2_sub$Coh)
df_comb_rnd2_sub$gene <- droplevels(df_comb_rnd2_sub$gene)
df_comb_rnd2_sub$Coh <- gsub("MPNST", "MPNST+GIST",df_comb_rnd2_sub$Coh)
df_comb_rnd2_sub$Coh <- gsub("NMELA", "EPIT",df_comb_rnd2_sub$Coh)
df_comb_rnd2_sub$Coh <- gsub("COMPLEX", "Complex Sarcomas",df_comb_rnd2_sub$Coh)
write.table(df_comb_rnd2_sub[,-10], "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/C345_gene_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)



##ISKS_MGRB, EPIT_MGRB and CAIRNS_MGRB without C3.
##no_C3
cpx_ISKS_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes_noC3, 1644, 3205, "ISKSvsMGRB"))
cpx_ISKS_complex_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_complex_mgrb_genes_noC3, 837, 3205, "COMPLEXvsMGRB"))
cpx_ISKS_tas_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_tas_mgrb_genes_noC3, 362, 3205, "TASvsMGRB"))
cpx_ISKS_simple_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_simple_mgrb_genes_noC3, 371, 3205, "SIMPLEvsMGRB"))
cpx_ISKS_mpnst_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mpnst_mgrb_genes_noC3, 157, 3205, "MPNSTvsMGRB"))
cpx_EPIT_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(epit_mgrb_genes_noC3, 835, 3205, "EPITvsMGRB"))

#cpx_NMELA_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(nmela_epit_mgrb_genes_noC3, 660, 3205, "NMELAvsMGRB"))
#cpx_MELA_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(mela_epit_mgrb_genes_noC3, 175, 3205, "MELAvsMGRB"))
cpx_NMELA_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(nmela_epit_mgrb_genes_noC3, 632, 3205, "NMELAvsMGRB"))
cpx_MELA_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(mela_epit_mgrb_genes_noC3, 203, 3205, "MELAvsMGRB"))

cpx_REPSET_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(sarc_comb_mgrb_genes_noC3, 563, 3205, "REPvsMGRB"))
#cpx_CAIRN_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(Cairns_noC3_fin, 413, 3205, "CAIRNvsMGRB"))
#noC3_df_comb_rnd2 <- rbind.data.frame(cpx_ISKS_OR_df_noC3, cpx_ISKS_complex_OR_df_noC3, 
#                                      cpx_ISKS_tas_OR_df_noC3,cpx_ISKS_simple_OR_df_noC3,
#                                      cpx_EPIT_OR_df_noC3, cpx_CAIRN_OR_df_noC3)
##without Cairns
noC3_df_comb_rnd2 <- rbind.data.frame(cpx_ISKS_OR_df_noC3, cpx_ISKS_complex_OR_df_noC3, 
                                      cpx_ISKS_tas_OR_df_noC3, cpx_ISKS_simple_OR_df_noC3, 
                                      cpx_ISKS_mpnst_OR_df_noC3, cpx_EPIT_OR_df_noC3, 
                                      cpx_NMELA_OR_df_noC3, cpx_MELA_OR_df_noC3,
                                      cpx_REPSET_OR_df_noC3)
noC3_df_comb_rnd2$pval_adj <- p.adjust(noC3_df_comb_rnd2$Fish_pval, 
                                       n = length(noC3_df_comb_rnd2$Fish_pval), method = "bonferroni")

noC3_df_comb_rnd2$Coh <- as.factor(gsub("vsMGRB", "", noC3_df_comb_rnd2$Coh))

noC3_df_comb_rnd2$OR_Fish <- ifelse(noC3_df_comb_rnd2$OR_Fish == 0, 1, noC3_df_comb_rnd2$OR_Fish)
noC3_df_comb_rnd2_filt <- noC3_df_comb_rnd2[noC3_df_comb_rnd2$Fish_pval < 0.05 & noC3_df_comb_rnd2$CI_lower > 1,]

##for heatmap
##C45
noC3_df_comb_rnd2_sub <- noC3_df_comb_rnd2[noC3_df_comb_rnd2$Coh %nin% c("TAS", "SIMPLE", "EPIT", "REP") &
                                         noC3_df_comb_rnd2$gene %in% c("Shelterin geneset", "Centrosome geneset", "BRCA geneset","TP53", "NF1 geneset"),]
noC3_df_comb_rnd2_sub$Coh <- droplevels(noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$gene <- droplevels(noC3_df_comb_rnd2_sub$gene)
noC3_df_comb_rnd2_sub$Coh <- gsub("MPNST", "MPNST+GIST",noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$Coh <- gsub("NMELA", "EPIT",noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$Coh <- gsub("COMPLEX", "Complex Sarcomas",noC3_df_comb_rnd2_sub$Coh)

write.table(noC3_df_comb_rnd2_sub[,-10], "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/C45_gene_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)


```

##Table for intra and intercohort comparisons:C45
```{r}
tab_noC3_multi_comp <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/C45_gene_complex_OR_sub.tsv", sep = "\t", header = T, stringsAsFactors = F)
inter_coh_fisher <- function(tab_dat, cpx_name, case_coh, cont_coh){
  if(case_coh %nin% cont_coh){
  cohs <- c(case_coh, cont_coh)
  df_sel <- tab_dat[tab_dat$gene %in% cpx_name & tab_dat$Coh %in% c(case_coh, cont_coh),c(2,8:9)]
  df_sel <- df_sel[match(cohs, df_sel$Coh),]
  inp <- c(df_sel[1,1], df_sel[1,2] - df_sel[1,1] , 
           df_sel[2,1], df_sel[2,2] - df_sel[2,1])
#  inp[3] <- ifelse(inp[3] == 0, 1, inp[3]) ##not needed, see below
#  https://stats.stackexchange.com/questions/198571/dealing-with-0-in-cell-count-for-fishers-exact-test

  sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
  colnames(sim_mat) <- c("case", "cont")
  rownames(sim_mat) <- c("hits", "no_hits")
  #ft <- fisher.test(sim_mat, alternative = "greater")
  #ft <- fisher.test(sim_mat)
  ft <- fisher.test(sim_mat, conf.int = T, conf.level = 0.95)
  ft_df <- cbind.data.frame("gene" = cpx_name ,"Cases" = df_sel[1,1],
                                 "Controls" = df_sel[2,1], "Case_Coh" = df_sel[1,2],
                                 "Cont_Coh" = df_sel[2,2], "Fish_pval" = ft$p.value,
                                 "CI_lower" = ft$conf.int[1],
                                 "CI_upper" = ft$conf.int[2],
                                 "OR_Fish" = ft$estimate, "Coh" = paste(cohs, collapse = "vs"))
  return(ft_df)
  }
  else {return(NULL)}
}

##C45
# ISKS_Sheltrin_cmp <- inter_coh_fisher(tab_noC3_multi_comp, cpx_name = "Shelterin geneset", case_coh = "ISKS", cont_coh = "EPIT")
# Complex_EPIT_Sheltrin_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Shelterin geneset", "Complex Sarcomas", "EPIT")
# Complex_ISKS_Sheltrin_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Shelterin geneset", "Complex Sarcomas", "ISKS")
# ISKS_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Centrosome geneset", "ISKS", "EPIT")
# MPNST_ISKS_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Centrosome geneset", "MPNST+GIST", "ISKS")
# MPNST_EPIT_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Centrosome geneset", "MPNST+GIST", "EPIT")
# MPNST_EPIT_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Centrosome geneset", "MPNST+GIST", "EPIT")
# 
# MPNST_EPIT_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "TP53", "ISKS", "Complex Sarcomas")
# MPNST_EPIT_Centro_cmp <- inter_coh_fisher(tab_noC3_multi_comp, "Centrosome geneset", "MPNST+GIST", "EPIT")
# 
# 
# fin_comb_tab <- rbind.data.frame(ISKS_Sheltrin_cmp, Complex_EPIT_Sheltrin_cmp, Complex_ISKS_Sheltrin_cmp, ISKS_Centro_cmp, MPNST_ISKS_Centro_cmp, MPNST_EPIT_Centro_cmp)
# fin_comb_tab$sig <- ifelse(fin_comb_tab$Fish_pval > 0.05, "ns", ifelse(fin_comb_tab$Fish_pval > 0.01 & fin_comb_tab$Fish_pval <= 0.05, "*",
#                            ifelse(fin_comb_tab$Fish_pval > 0.001 & fin_comb_tab$Fish_pval <= 0.01, "**",
#                            ifelse(fin_comb_tab$Fish_pval > 0.0001 & fin_comb_tab$Fish_pval <= 0.001, "***", "****"))))

#write.table(fin_comb_tab, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/intra_intercoh_C45_gene_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)

##All vs All; run only for C4/5
cont_cohs <- c("ISKS", "Complex Sarcomas", "MPNST+GIST", "EPIT", "MELA")
case_cohs <- c("ISKS", "Complex Sarcomas", "MPNST+GIST", "EPIT", "MELA")


multi_inter_coh <- function(tab, cases, controls, cpx_name){
all_comp <- list()
all_comp_sub <- list()
for(m in 1:length(controls)){
 # print(m)
  for(n in 1:length(cases)){
 #   print(cases[n])
    all_comp_sub[[n]] <- inter_coh_fisher(tab_dat = tab, cpx_name = cpx_name,  case_coh = cases[n], 
                                          cont_coh = controls[m])
  }
  all_comp[[m]] <- do.call("rbind.data.frame", all_comp_sub)
}
all_comp_df <- do.call("rbind.data.frame", all_comp)
return(all_comp_df)
#return(all_comp)
}
##C45
Sheltrin_cmp <- multi_inter_coh(tab_noC3_multi_comp, case_cohs, cont_cohs, "Shelterin geneset")
Centrosome_cmp <- multi_inter_coh(tab_noC3_multi_comp, case_cohs, cont_cohs, "Centrosome geneset")
NF1_cmp <- multi_inter_coh(tab_noC3_multi_comp, case_cohs, cont_cohs, "NF1 geneset")
BRCA_cmp <- multi_inter_coh(tab_noC3_multi_comp, case_cohs, cont_cohs, "BRCA geneset")
TP53_cmp <- multi_inter_coh(tab_noC3_multi_comp, case_cohs, cont_cohs, "TP53")
fin_comb_tab <- rbind.data.frame(Sheltrin_cmp, Centrosome_cmp, NF1_cmp, BRCA_cmp, TP53_cmp)

fin_comb_tab$sig <- ifelse(fin_comb_tab$Fish_pval > 0.05, "ns", ifelse(fin_comb_tab$Fish_pval > 0.01 & fin_comb_tab$Fish_pval <= 0.05, "*",ifelse(fin_comb_tab$Fish_pval > 0.001 & fin_comb_tab$Fish_pval <= 0.01, "**",ifelse(fin_comb_tab$Fish_pval > 0.0001 & fin_comb_tab$Fish_pval <= 0.001, "***", "****"))))

##Filter out ns and OR < 1
fin_comb_tab_filt <- fin_comb_tab[fin_comb_tab$sig %nin% "ns" & fin_comb_tab$OR_Fish > 1,]
fin_comb_tab_filt <- unique(fin_comb_tab_filt)
write.table(fin_comb_tab_filt, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/All_intra_intercoh_C45_gene_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)

write.table(fin_comb_tab, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/All_unfilt_intra_intercoh_C45_gene_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)

```


##Heatmaps with C45 variants
```{r echo=FALSE, warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}
################heatmap (ISKS vs MGRB)
tab_noC3 <- noC3_df_comb_rnd2_sub
tab_noC3$Coh <- factor(tab_noC3$Coh, levels = unique(tab_noC3$Coh))
tab_noC3$sig <- ifelse(tab_noC3$Fish_pval > 0.05, "ns", ifelse(tab_noC3$Fish_pval > 0.01 & tab_noC3$Fish_pval <= 0.05, "*",
                                                               ifelse(tab_noC3$Fish_pval > 0.001 & tab_noC3$Fish_pval <= 0.01, "**",
                                                                      ifelse(tab_noC3$Fish_pval > 0.0001 & tab_noC3$Fish_pval <= 0.001, "***", "****"))))

##Add dendrogram to heatmap
library("ggplot2")
library("ggdendro")
library("reshape2")
library("grid")
##C45 subset complex and cohorts

tab_noC3$Coh <- droplevels(tab_noC3$Coh)
#tab_noC3$gene <- droplevels(tab_noC3$gene)
tab_noC3$Coh <- factor(x = tab_noC3$Coh,
                           levels =c("ISKS", "Complex Sarcomas", "MPNST+GIST",
                                     "EPIT", "MELA") , 
                           ordered = TRUE)
df_dendro <- tab_noC3[,c(1,9,7)]
df_dendro$OR_Fish <- ifelse(is.infinite(df_dendro$OR_Fish), 0, df_dendro$OR_Fish) 
df_dendro.scaled <- df_dendro
df_dendro.scaled[, 3] <- scale(df_dendro.scaled[, 3])
df_dendro_mat <- acast(df_dendro.scaled, gene ~ Coh)
dend_inp <- as.dendrogram(hclust(d = dist(x = df_dendro_mat))) 

# Create dendro
dendro.plot <- ggdendrogram(data = dend_inp, rotate = TRUE) + 
  theme(axis.text.y = element_text(face="bold", size=10)) + theme(axis.text.x = element_blank())

# Preview the plot
print(dendro.plot)

##order heatmap
dend_inp.order <- order.dendrogram(dend_inp)
tab_noC3$gene <- factor(x = tab_noC3$gene,
                            levels = tab_noC3$gene[dend_inp.order], ordered = TRUE)
##C45
p1 <- ggplot(tab_noC3, aes(Coh, gene, fill= log2(OR_Fish))) + geom_tile() + theme_minimal()
p1_order <- p1 + scale_fill_distiller(palette = "RdBu") + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.text.x = element_text(face="bold", size=10)) +
  theme(axis.title.x=element_blank()) + 
  theme(axis.text.x = element_text(margin = margin(t = 5))) + 
  theme(legend.position="top") + geom_text(aes(label = sig)) + 
  theme(axis.text.y = element_blank()) + theme(axis.title.y=element_blank())
grid.newpage()
print(p1_order, vp = viewport(x = 0.4, y = 0.5, width = 0.8, height = 1.0))
print(dendro.plot, vp = viewport(x = 0.85, y = 0.44, width = 0.15, height = 0.81))

##Heatmap without dendrogram

tab_noC3$gene <- factor(x = tab_noC3$gene,
                            levels = c("Centrosome geneset","NF1 geneset", "Shelterin geneset", "BRCA geneset","TP53"), ordered = TRUE)
p2 <- ggplot(tab_noC3, aes(Coh, gene, fill= log2(OR_Fish))) + geom_tile() + theme_minimal()
p2_order <- p2 + scale_fill_distiller(palette = "RdBu") + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.text.x = element_text(face="bold", size=10)) +
  theme(axis.title.x=element_blank()) + 
  theme(axis.text.x = element_text(margin = margin(t = 5))) +
  theme(axis.text.y = element_text(face="bold", size=10)) + 
  theme(legend.position="right", legend.title=element_text(size=8)) + 
  geom_text(aes(label = sig)) + 
  theme(axis.title.y=element_blank())

#p2_order <- p2_order + guides(fill=guide_legend(title="Log2(OR)"))
p2_order

```

##Heatmap C345 variants
```{r echo=FALSE, warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}
tab_C345 <- df_comb_rnd2_sub
tab_C345$Coh <- factor(tab_C345$Coh, levels = unique(tab_C345$Coh))
tab_C345$sig <- ifelse(tab_C345$Fish_pval > 0.05, "ns", ifelse(tab_C345$Fish_pval > 0.01 & tab_C345$Fish_pval <= 0.05, "*",
                                                               ifelse(tab_C345$Fish_pval > 0.001 & tab_C345$Fish_pval <= 0.01, "**",
                                                                      ifelse(tab_C345$Fish_pval > 0.0001 & tab_C345$Fish_pval <= 0.001, "***", "****"))))

##Add dendrogram to heatmap
library("ggplot2")
library("ggdendro")
library("reshape2")
library("grid")
##C45 subset complex and cohorts
tab_C345$OR_Fish <- ifelse(is.infinite(tab_C345$OR_Fish), 0, tab_C345$OR_Fish) 
tab_C345$Coh <- droplevels(tab_C345$Coh)
#tab_C345$gene <- droplevels(tab_C345$gene)
#tab_C345$gene <- as.factor(tab_C345$gene)
tab_C345$Coh <- factor(x = tab_C345$Coh,
                       levels =c("ISKS", "Complex Sarcomas", "MPNST+GIST",
                                 "EPIT", "MELA") , 
                       ordered = TRUE)
df_dendro <- tab_C345[,c(1,9,7)]
df_dendro$OR_Fish <- ifelse(is.infinite(df_dendro$OR_Fish), 0, df_dendro$OR_Fish) 
df_dendro.scaled <- df_dendro
df_dendro.scaled[, 3] <- scale(df_dendro.scaled[, 3])
df_dendro_mat <- acast(df_dendro.scaled, gene ~ Coh)
dend_inp <- as.dendrogram(hclust(d = dist(x = df_dendro_mat))) 

# Create dendro
dendro.plot <- ggdendrogram(data = dend_inp, rotate = TRUE) + 
  theme(axis.text.y = element_text(face="bold", size=10))

# Preview the plot
print(dendro.plot)

##order heatmap
dend_inp.order <- order.dendrogram(dend_inp)
tab_C345$gene <- factor(x = tab_C345$gene,
                        levels = tab_C345$gene[dend_inp.order], 
                        ordered = TRUE)
##C345
p1 <- ggplot(tab_C345, aes(Coh, gene, fill= log2(OR_Fish))) + geom_tile() + theme_minimal()
p1_order <- p1 + scale_fill_distiller(palette = "RdBu") + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.text.x = element_text(face="bold", size=10)) +
  theme(axis.title.x=element_blank()) + 
  theme(axis.text.x = element_text(margin = margin(t = 5))) + 
  theme(legend.position="top") + geom_text(aes(label = sig)) + 
  theme(axis.text.y = element_blank()) + theme(axis.title.y=element_blank())
grid.newpage()
print(p1_order, vp = viewport(x = 0.4, y = 0.5, width = 0.8, height = 1.0))
print(dendro.plot, vp = viewport(x = 0.85, y = 0.44, width = 0.15, height = 0.81))

##Heatmap without dendrogram

tab_C345$gene <- factor(x = tab_C345$gene,
                            levels = c("Centrosome geneset","NF1 geneset", "Shelterin geneset", "BRCA geneset","TP53"), ordered = TRUE)
p2_C345 <- ggplot(tab_C345, aes(Coh, gene, fill= log2(OR_Fish))) + geom_tile() + theme_minimal()
p2_order_C345 <- p2 + scale_fill_distiller(palette = "RdBu") + 
  theme(axis.text.x = element_text(angle = 0)) + 
  theme(axis.text.x = element_text(face="bold", size=10)) +
  theme(axis.title.x=element_blank()) + 
  theme(axis.text.x = element_text(margin = margin(t = 5))) +
  theme(axis.text.y = element_text(face="bold", size=10)) + 
  #theme(legend.position="top") +
  theme(legend.position="right", legend.title=element_text(size=8)) + 
  geom_text(aes(label = sig)) + 
  theme(axis.title.y=element_blank())

#p2_order <- p2_order + guides(fill=guide_legend(title="Log2(OR)"))
p2_order_C345

```

##Validation stage 1 :C45 and C345
##2-fold Cross validation(Master script Aug31_freeze/Replication/fisher_rep_test_permute.R)

```{r echo=FALSE, warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}

##rename complexes

names(cpx_list) <- c("Shelterin", "Glutamate_NMDA", "ZBTB16_complex", "CEP_HAUS_core", "CEP_HAUS_extn1", 
                     "CEP_HAUS_SKAT", "CEP_HAUS_Biogrid", "CENP_complex", "TCP1_complex", "PRPF4_complex", "BRCA_genes", "SARC_genes", "Centrosome_genes", "mito_HSA_69278", "mito_chk_GO", "mito_43", "cent_rep_genes",
                     "TP53_control", "MPNST_pos")
############C45
##Mantel-Haenszel method (more Robust)
CI_meta_MH_data <- function(cmpx_name){
  library(meta)
  library(metafor)
  df1_disc <- read.delim(paste0("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Validation_new_cpx/",cmpx_name,"_fisher.disc_null.tsv"),
                         sep = "\t", header = T, stringsAsFactors = F )
  df1_rep <- read.delim(paste0("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Validation_new_cpx/",cmpx_name,"_fisher.rep_null.tsv"),
                        sep = "\t", header = T, stringsAsFactors = F )
  comb_Mant_fun <- function(df){
    fixed_mod <- metabin(Cases, Cases_comp, Controls, Controls_comp, data = df,  
                         studlab = gene,
                         method.tau = "SJ",
                         comb.fixed = FALSE,
                         comb.random = TRUE,
                         hakn = TRUE,
                         prediction = TRUE,
                         incr = 0.1,
                         sm = "OR")
    summ <- summary(fixed_mod)
    
 #   ret_df <- cbind.data.frame("cmpx_name" = cmpx_name, "Fish_OR_meta" = exp(summ$fixed$TE), 
 #                              "lower.CI" = exp(summ$fixed$lower), "upper.CI" = exp(summ$fixed$upper))
  ##use prediction interval for the forest plot
    #https://www.erim.eur.nl/research-support/meta-essentials/interpret-results/the-forest-plot/prediction-interval/
    #https://bmjopen.bmj.com/content/6/7/e010247
     ret_df <- cbind.data.frame("cmpx_name" = cmpx_name, "Fish_OR_meta" = exp(summ$random$TE), 
                               "lower.CI" = exp(summ$predict$lower), "upper.CI" = exp(summ$predict$upper),
                               "comb_pval" = summ$random$p)
    
  }
  
  
  return(list(comb_Mant_fun(df1_disc), comb_Mant_fun(df1_rep)))
  
}

CI_MH_meta <- list()
for(i in 1:length(cpx_list)){
  CI_MH_meta[[i]] <- CI_meta_MH_data(names(cpx_list)[i])
}

library(ggplot2)
CI_disc_MH_meta <- lapply(CI_MH_meta, function(x)x[[1]])
CI_disc_MH_meta_df <- do.call("rbind.data.frame", CI_disc_MH_meta)
CI_disc_MH_meta_df$set <- "Disc"
CI_rep_MH_meta <- lapply(CI_MH_meta, function(x)x[[2]])
CI_rep_MH_meta_df <- do.call("rbind.data.frame", CI_rep_MH_meta)
CI_rep_MH_meta_df$set <- "Rep"

CI_comb_MH_meta_df <- rbind.data.frame(CI_disc_MH_meta_df, CI_rep_MH_meta_df)
#CI_comb_MH_meta_df$Index <- rownames(CI_comb_MH_meta_df)

# xname <- expression(paste(italic("Log"), "OR"))
#setting up the basic plot
# p_meta <- ggplot(data=CI_comb_MH_meta_df, aes(y=cmpx_name, x=log2(Fish_OR_meta), xmin=log2(lower.CI), xmax=log2(upper.CI))) + 
#   geom_point() + geom_point(data=subset(CI_comb_MH_meta_df, set=="Disc"), color="Black", size=2) + 
#   geom_errorbarh(height=.1) + scale_x_continuous(limits=c(-2,5), breaks = c(-2:5), name=xname) +
#   geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) + 
#   facet_grid(set~., scales= "free", space="free") + ggtitle("PPI cliques")+
#   theme_minimal() + theme(text=element_text(family="Times",size=18, color="black"))+
#   theme(panel.spacing = unit(1, "lines"))

#p_meta

# ##For supp figure
#CI_comb_MH_meta_df_sub <- CI_comb_MH_meta_df[CI_comb_MH_meta_df$cmpx_name %in% c("SARC_genes","TP53_control", "Shelterin","CEP_HAUS_core"),]
##remove SARC_genes (Oct.17.2020)
CI_comb_MH_meta_df_sub <- CI_comb_MH_meta_df[CI_comb_MH_meta_df$cmpx_name %in% c("TP53_control", "Shelterin","CEP_HAUS_core"),]
CI_comb_MH_meta_df_sub$cmpx_name <- gsub("CEP_HAUS_core", "Centrosome geneset",CI_comb_MH_meta_df_sub$cmpx_name)
CI_comb_MH_meta_df_sub$cmpx_name <- gsub("Shelterin", "Shelterin geneset",CI_comb_MH_meta_df_sub$cmpx_name)
#CI_comb_MH_meta_df_sub$cmpx_name <- gsub("SARC_genes", "Sarcoma geneset",CI_comb_MH_meta_df_sub$cmpx_name)
CI_comb_MH_meta_df_sub$cmpx_name <- gsub("TP53_control", "TP53",CI_comb_MH_meta_df_sub$cmpx_name)
#CI_comb_MH_meta_df_sub$cmpx_name <- gsub("MPNST_pos", "NF1 geneset",CI_comb_MH_meta_df_sub$cmpx_name)
write.table(CI_comb_MH_meta_df_sub, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/CV_2fold_disc_rep.tsv", sep = "\t", quote = F, row.names = F)

colnames(CI_comb_MH_meta_df_sub)[6] <- "Coh"
CI_comb_MH_meta_df_sub$Coh <- gsub("Disc", "2/3 split", CI_comb_MH_meta_df_sub$Coh)
CI_comb_MH_meta_df_sub$Coh <- gsub("Rep", "1/3 split", CI_comb_MH_meta_df_sub$Coh)
CI_comb_MH_meta_df_sub$Coh <- as.factor(CI_comb_MH_meta_df_sub$Coh)
CI_comb_MH_meta_df_sub$cmpx_name <- factor(x = CI_comb_MH_meta_df_sub$cmpx_name,
                            levels = c("Centrosome geneset","Shelterin geneset", "TP53"), ordered = TRUE)


# p_sub <- ggplot(data=CI_comb_MH_meta_df_sub, aes(y=cmpx_name, x=log2(Fish_OR_meta), xmin=log2(lower.CI), xmax=log2(upper.CI))) +
#   geom_point() + geom_point(data=subset(CI_comb_MH_meta_df_sub, set=="Disc"), color="Black", size=2) +
#   geom_errorbarh(height=.1) + scale_x_continuous(limits=c(-2,4), breaks = c(-2:4), name=xname) +
#   geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) +
#   facet_grid(set~., scales= "free", space="free") + ggtitle("PPI cliques")+
#   theme_minimal() + theme(text=element_text(family="Times",size=18, color="black"))+
#   theme(panel.spacing = unit(1, "lines"))

#p_sub

##Alternate plotting##use this
#https://aosmith.rbind.io/2018/01/19/reversing-the-order-of-a-ggplot2-legend/
# library(ggplot2)
# forest_custplot <- function(df){
#   dotCOLS = c("#030000", "#030000")
#   barCOLS = c("#030000", "#030000")
#   p <- ggplot(df, aes(x=cmpx_name, y=log2(Fish_OR_meta), ymin=log2(lower.CI), ymax=log2(upper.CI),col=Coh,fill=Coh)) + 
#     #specify position here
#     geom_linerange(size=1,position=position_dodge(width = 0.6)) +
#     geom_hline(yintercept=0, lty=2) +
#     #specify position here too
#     geom_point(size=4, aes(shape = Coh, color = Coh), position=position_dodge(width = 0.6)) +
#   #  geom_point(size=4, aes(color = Coh), position=position_dodge(width = 0.6)) +
# #    geom_point(aes(size=5, shape=21, colour="white", stroke = 0.5,position=position_dodge(width = #0.5)) +
#     scale_fill_manual(values=barCOLS)+
#     scale_color_manual(values=dotCOLS)+
#     scale_x_discrete(name="") + 
#     scale_y_continuous(name="Enrichment in ISKS compared to controls [Log2 Odds ratio]",seq(0, 7, by = 1)) +
#     coord_flip() #+
#   #  theme_minimal() + theme(legend.position="bottom") + theme(legend.title = element_blank()) +
#   #  theme(legend.text = element_text(size=8))
#   return(p)
# }


#TP53, Shelterin geneset, Centrosome geneset
#CI_comb_MH_meta_df_sub$Coh <- factor(CI_comb_MH_meta_df_sub$Coh, levels = c("Rep", "Disc"), ordered = TRUE)
# p_forest <- forest_custplot(CI_comb_MH_meta_df_sub) + ggtitle("Cross validation C45") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) + scale_shape_manual(values = c(15,19)) + theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(axis.line.x = element_line(color="black", size = 1)) + theme(legend.position = "right") + theme(axis.title.y = element_blank()) 
# 
# p_forest 
##new approach to reverse legend
library(ggplot2)
forest_custplot <- function(df){
  g1 = ggplot(df, aes(x = cmpx_name, y = log2(Fish_OR_meta), group = Coh) ) +
  #  geom_point(position = position_dodge(width = .75) ) +
    geom_point(size=4, aes(shape = Coh), position=position_dodge(width = 0.6)) + 
    geom_errorbar( aes(ymin = log2(lower.CI), ymax = log2(upper.CI),
                       linetype = Coh,
                       width = c(.1, .1, .1, .1, .1, 0.1) ),
                   position = position_dodge(width = .6) ) +
      theme_bw() + 
      labs(y = "Enrichment in ISKS compared to controls [Log2 Odds ratio]",
           x = "") +
     # geom_rect(xmin = -Inf, xmax = Inf, ymin = -.25, ymax = .25, 
      #      fill = "grey54", alpha = .05) +
      scale_y_continuous(breaks = seq(0, 7, by = 1) ) + 
      coord_flip() +
      scale_linetype_manual(values = c("solid", "solid"),
                            name = element_blank(),
                            labels = c("1/3 split", "2/3 split") ) + 
     scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("1/3 split", "2/3 split") ) 
return(g1)
}
CI_comb_MH_meta_df_sub$Coh = factor(CI_comb_MH_meta_df_sub$Coh, levels = c("1/3 split", "2/3 split") )

g1 <- forest_custplot(CI_comb_MH_meta_df_sub)

g2 <- g1 %+% 
     CI_comb_MH_meta_df_sub +
     scale_linetype_manual(values = c("solid", "solid"),
                           name = element_blank(),
                           labels = c("1/3 split", "2/3 split"),
                           guide = guide_legend(reverse = TRUE) ) + scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("1/3 split", "2/3 split"), guide = guide_legend(reverse = TRUE) )

p_forest <- g2 + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank())

p_forest <- p_forest + ggtitle("Cross validation C45") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) +  theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(axis.line.x = element_line(color="black", size = 1)) + theme(legend.position = "right") +
  geom_hline(yintercept = 0, lty = 2)

p_forest
############C345
##Mantel-Haenszel method (more Robust)
CI_meta_MH_data_C345 <- function(cmpx_name){
  library(meta)
  library(metafor)
  df1_disc <- read.delim(paste0("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Validation_new_cpx/",cmpx_name,"_C345_fisher.disc_null.tsv"),
                         sep = "\t", header = T, stringsAsFactors = F )
  df1_rep <- read.delim(paste0("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Validation_new_cpx/",cmpx_name,"_C345_fisher.rep_null.tsv"),
                        sep = "\t", header = T, stringsAsFactors = F )
  comb_Mant_fun <- function(df){
    fixed_mod <- metabin(Cases, Cases_comp, Controls, Controls_comp, data = df,  
                         studlab = gene,
                         method.tau = "SJ",
                         comb.fixed = FALSE,
                         comb.random = TRUE,
                         hakn = TRUE,
                         prediction = TRUE,
                         incr = 0.1,
                         sm = "OR")
    summ <- summary(fixed_mod)
    
 #   ret_df <- cbind.data.frame("cmpx_name" = cmpx_name, "Fish_OR_meta" = exp(summ$fixed$TE), 
 #                              "lower.CI" = exp(summ$fixed$lower), "upper.CI" = exp(summ$fixed$upper))
  ##use prediction interval for the forest plot
    #https://www.erim.eur.nl/research-support/meta-essentials/interpret-results/the-forest-plot/prediction-interval/
    #https://bmjopen.bmj.com/content/6/7/e010247
    ret_df <- cbind.data.frame("cmpx_name" = cmpx_name, "Fish_OR_meta" = exp(summ$random$TE), 
                               "lower.CI" = exp(summ$predict$lower), "upper.CI" = exp(summ$predict$upper),
                               "comb_pval" = summ$random$p)
  }
  
  
  return(list(comb_Mant_fun(df1_disc), comb_Mant_fun(df1_rep)))
  
}

CI_MH_meta <- list()
for(i in 1:length(cpx_list)){
  CI_MH_meta[[i]] <- CI_meta_MH_data_C345(names(cpx_list)[i])
}

library(ggplot2)
CI_disc_MH_meta_345 <- lapply(CI_MH_meta, function(x)x[[1]])
CI_disc_MH_meta_345_df <- do.call("rbind.data.frame", CI_disc_MH_meta_345)
CI_disc_MH_meta_345_df$set <- "Disc"
CI_rep_MH_meta_345 <- lapply(CI_MH_meta, function(x)x[[2]])
CI_rep_MH_meta_345_df <- do.call("rbind.data.frame", CI_rep_MH_meta_345)
CI_rep_MH_meta_345_df$set <- "Rep"

CI_comb_MH_meta_C345_df <- rbind.data.frame(CI_disc_MH_meta_345_df, CI_rep_MH_meta_345_df)

# ##For supp figure
CI_comb_MH_meta_C345_df_sub <- CI_comb_MH_meta_C345_df[CI_comb_MH_meta_C345_df$cmpx_name %in% c("TP53_control", "Shelterin","CEP_HAUS_core"),]
CI_comb_MH_meta_C345_df_sub$cmpx_name <- gsub("CEP_HAUS_core", "Centrosome geneset",CI_comb_MH_meta_C345_df_sub$cmpx_name)
CI_comb_MH_meta_C345_df_sub$cmpx_name <- gsub("Shelterin", "Shelterin geneset",CI_comb_MH_meta_C345_df_sub$cmpx_name)
#CI_comb_MH_meta_C345_df_sub$cmpx_name <- gsub("SARC_genes", "Sarcoma geneset",CI_comb_MH_meta_C345_df_sub$cmpx_name)
CI_comb_MH_meta_C345_df_sub$cmpx_name <- gsub("TP53_control", "TP53",CI_comb_MH_meta_C345_df_sub$cmpx_name)
#CI_comb_MH_meta_df_sub$cmpx_name <- gsub("MPNST_pos", "NF1 geneset",CI_comb_MH_meta_df_sub$cmpx_name)
write.table(CI_comb_MH_meta_C345_df_sub, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/CV_2fold_disc_rep_C345.tsv", sep = "\t", quote = F, row.names = F)

colnames(CI_comb_MH_meta_C345_df_sub)[6] <- "Coh"
CI_comb_MH_meta_C345_df_sub$Coh <- gsub("Disc", "2/3 split", CI_comb_MH_meta_C345_df_sub$Coh)
CI_comb_MH_meta_C345_df_sub$Coh <- gsub("Rep", "1/3 split", CI_comb_MH_meta_C345_df_sub$Coh)
CI_comb_MH_meta_C345_df_sub$Coh <- as.factor(CI_comb_MH_meta_C345_df_sub$Coh)
CI_comb_MH_meta_C345_df_sub$cmpx_name <- factor(x = CI_comb_MH_meta_C345_df_sub$cmpx_name,
                            levels = c("Centrosome geneset","Shelterin geneset", "TP53"), ordered = TRUE)
##Alternate plotting##use this

g1_C345 <- forest_custplot(CI_comb_MH_meta_C345_df_sub)

CI_comb_MH_meta_C345_df_sub$Coh = factor(CI_comb_MH_meta_C345_df_sub$Coh, levels = c("1/3 split", "2/3 split") )

g2_C345 <- g1_C345 %+% 
     CI_comb_MH_meta_C345_df_sub +
     scale_linetype_manual(values = c("solid", "solid"),
                           name = element_blank(),
                           labels = c("1/3 split", "2/3 split"),
                           guide = guide_legend(reverse = TRUE) ) + scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("1/3 split", "2/3 split"), guide = guide_legend(reverse = TRUE) )

#c("1/3 split", "2/3 split")

p_forest_CV_345 <- g2_C345 + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank())

p_forest_CV_345 <- p_forest_CV_345 + ggtitle("Cross validation C345") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) +  theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(axis.line.x = element_line(color="black", size = 1)) +
  geom_hline(yintercept = 0, lty = 2)

p_forest_CV_345


```


##flexible foresplot(used above; ignore chunk)
```{r echo=FALSE}
( g1 = ggplot(CI_comb_MH_meta_df_sub, aes(x = cmpx_name, y = log2(Fish_OR_meta), group = Coh) ) +
  #  geom_point(position = position_dodge(width = .75) ) +
    geom_point(size=4, aes(shape = Coh), position=position_dodge(width = 0.6)) + 
    geom_errorbar( aes(ymin = log2(lower.CI), ymax = log2(upper.CI),
                       linetype = Coh,
                       width = c(.2, .2, .2, .2, .2, 0.2) ),
                   position = position_dodge(width = .6) ) +
      theme_bw() + 
      labs(y = "Enrichment in ISKS compared to controls [Log2 Odds ratio]",
           x = "") +
     # geom_rect(xmin = -Inf, xmax = Inf, ymin = -.25, ymax = .25, 
      #      fill = "grey54", alpha = .05) +
      scale_y_continuous(breaks = seq(0, 7, by = 1) ) + 
      coord_flip() +
      scale_linetype_manual(values = c("solid", "solid"),
                            name = element_blank(),
                            labels = c("Rep", "Disc") ) + 
     scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("Rep", "Disc") ) )

CI_comb_MH_meta_df_sub$Coh = factor(CI_comb_MH_meta_df_sub$Coh, levels = c("Rep", "Disc") )


g2 <- g1 %+% 
     CI_comb_MH_meta_df_sub +
     scale_linetype_manual(values = c("solid", "solid"),
                           name = element_blank(),
                           labels = c("Rep", "Disc"),
                           guide = guide_legend(reverse = TRUE) ) + scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("Rep", "Disc"), guide = guide_legend(reverse = TRUE) )

g3 <- g2 + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank())

```


##Validation stage 2 : C45, C345
##replication set(Augmented replication set; Master script Aug31_freeze/Replication/gene_cmx_cmp_repset.R)
```{r echo=FALSE, warning = FALSE}
##inherits object cpx_list from chunk1
##rename complexes

names(cpx_list) <- c("Shelterin", "Glutamate_NMDA", "ZBTB16_complex", "CEP_HAUS_core", "CEP_HAUS_extn1", 
                     "CEP_HAUS_SKAT", "CEP_HAUS_Biogrid", "CENP_complex", "TCP1_complex", "PRPF4_complex", "BRCA_genes", "SARC_genes", "Centrosome_genes", "mito_HSA_69278", "mito_chk_GO", "mito_43", "cent_rep_genes",
                     "TP53_control", "MPNST_pos")
##Augmented replication sets (the variants here have been trimmed based on the BED coordinates of exome kit)
#CEP_HAUS_core_rep <- c("CEP63", "CEP72", "HAUS4", "HAUS5")
#cpx_list[[20]] <- CEP_HAUS_core_rep
#names(cpx_list)[20] <- c("CEP_HAUS_core_rep")

isks_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_mgrb_all.rds")
isks_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_mgrb_all_noC3.rds")


## (subsetted with PID genes)
repset_563 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_563.rds")
repset_563_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_563_noC3.rds")

repset_663 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_663.rds")
repset_663_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_663_noC3.rds")

repset_763 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_763.rds")
repset_763_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_763_noC3.rds")

repset_963 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_963.rds")
repset_963_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/repset_963_noC3.rds")

##ISKS complemented have the exome coordinates of discovery set NOT replication set
##ISKS noC3 complemented
isks_min100_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min100_noC3.rds")
isks_min200_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min200_noC3.rds")
isks_min400_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min400_noC3.rds")

##ISKS C345 complemented
isks_min100 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min100.rds")
isks_min200 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min200.rds")
isks_min400 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/Comb_TCGA_BERG_NoSarc/augmented_sarc/isks_min400.rds")

########

cpx_OR_fisher <- function(ppi_res,case_coh_size, cont_coh_size, coh){
  ft_df <- list()
  for(i in 1:length(cpx_list)){
    ppi_res_tab <- ppi_res[as.character(ppi_res$gene) %in% cpx_list[[i]],]
   # ppi_res_tab[,2] <- ifelse(ppi_res_tab[,2] == 0, 1, ppi_res_tab[,2])
    inp <- c(sum(ppi_res_tab[,1]), case_coh_size - sum(ppi_res_tab[,1]) , 
             sum(ppi_res_tab[,2]), cont_coh_size - sum(ppi_res_tab[,2]))
    sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
    colnames(sim_mat) <- c("case", "cont")
    rownames(sim_mat) <- c("hits", "no_hits")
    #ft <- fisher.test(sim_mat, alternative = "greater")
    ft <- fisher.test(sim_mat)
    ft <- fisher.test(sim_mat, conf.int = T, conf.level = 0.95)
    ft_df[[i]] <- cbind.data.frame("gene" = names(cpx_list)[i] ,"Cases" = sum(ppi_res_tab[,1]),
                                   "Controls" = sum(ppi_res_tab[,2]),
                                   "Fish_pval" = ft$p.value,"CI_lower" = ft$conf.int[1],
                                   "CI_upper" = ft$conf.int[2],
                                   "OR_Fish" = ft$estimate, "Coh" = coh)
  }
  return(ft_df)
}


cpx_ISKS_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes, 1644, 3205, "ISKSvsMGRB"))
cpx_isks_min100 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min100, 1544, 3205, "ISKS100vsMGRB"))
cpx_isks_min200 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min200, 1444, 3205, "ISKS200vsMGRB"))
cpx_isks_min400 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min400, 1244, 3205, "ISKS400vsMGRB"))

cpx_repset_563 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_563, 563, 3205, "rep563vsMGRB"))
cpx_repset_663 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_663, 663, 3205, "rep663vsMGRB"))
cpx_repset_763 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_763, 763, 3205, "rep763vsMGRB"))
cpx_repset_963 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_963, 963, 3205, "rep963vsMGRB"))

df_comb_rnd2 <- rbind.data.frame(cpx_ISKS_OR_df, cpx_isks_min100, cpx_isks_min200, cpx_isks_min400,
                                 cpx_repset_563, cpx_repset_663, cpx_repset_763, cpx_repset_963)
df_comb_rnd2$Coh <- as.factor(gsub("vsMGRB", "", df_comb_rnd2$Coh))
df_comb_rnd2_filt <- df_comb_rnd2[df_comb_rnd2$Fish_pval < 0.05, ]

##ISKS_MGRB, EPIT_MGRB and CAIRNS_MGRB without C3.
##no_C3
cpx_ISKS_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes_noC3, 1644, 3205, "ISKSvsMGRB"))
cpx_isks_min100_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min100_noC3, 1544, 3205, "ISKS100vsMGRB"))
cpx_isks_min200_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min200_noC3, 1444, 3205, "ISKS200vsMGRB"))
cpx_isks_min400_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_min400_noC3, 1244, 3205, "ISKS400vsMGRB"))

cpx_repset_563_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_563_noC3, 563, 3205, "rep563vsMGRB"))
cpx_repset_663_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_663_noC3, 663, 3205, "rep663vsMGRB"))
cpx_repset_763_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_763_noC3, 763, 3205, "rep763vsMGRB"))
cpx_repset_963_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(repset_963_noC3, 963, 3205, "rep963vsMGRB"))

noC3_df_comb_rnd2 <- rbind.data.frame(cpx_ISKS_OR_df_noC3, cpx_isks_min100_noC3, 
                                      cpx_isks_min200_noC3,cpx_isks_min400_noC3,
                                      cpx_repset_563_noC3, cpx_repset_663_noC3,
                                      cpx_repset_763_noC3, cpx_repset_963_noC3)
noC3_df_comb_rnd2$pval_adj <- p.adjust(noC3_df_comb_rnd2$Fish_pval, 
                                       n = length(noC3_df_comb_rnd2$Fish_pval), method = "bonferroni")

noC3_df_comb_rnd2$Coh <- as.factor(gsub("vsMGRB", "", noC3_df_comb_rnd2$Coh))

noC3_df_comb_rnd2$OR_Fish <- ifelse(noC3_df_comb_rnd2$OR_Fish == 0, 1, noC3_df_comb_rnd2$OR_Fish)
noC3_df_comb_rnd2_filt <- noC3_df_comb_rnd2[noC3_df_comb_rnd2$Fish_pval < 0.05 & noC3_df_comb_rnd2$CI_lower > 1,]

##C45
##removed Sarcoma geneset; Oct17-2020
noC3_df_comb_rnd2_sub <- noC3_df_comb_rnd2[noC3_df_comb_rnd2$Coh %in% c("ISKS200", "rep763") &
                                         noC3_df_comb_rnd2$gene %in% c("Shelterin", "CEP_HAUS_core",
                                                                       "TP53_control"),]
noC3_df_comb_rnd2_sub$Coh <- droplevels(noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$gene <- droplevels(noC3_df_comb_rnd2_sub$gene)
noC3_df_comb_rnd2_sub$gene <- gsub("CEP_HAUS_core","Centrosome geneset",noC3_df_comb_rnd2_sub$gene)
noC3_df_comb_rnd2_sub$gene <- gsub("Shelterin", "Shelterin geneset",noC3_df_comb_rnd2_sub$gene)
#noC3_df_comb_rnd2_sub$gene <- gsub("SARC_genes", "Sarcoma geneset",noC3_df_comb_rnd2_sub$gene)
noC3_df_comb_rnd2_sub$gene <- gsub("TP53_control", "TP53",noC3_df_comb_rnd2_sub$gene)


write.table(noC3_df_comb_rnd2_sub[,-9], "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/C45_aug_repset_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)

noC3_df_comb_rnd2_sub$Coh <- gsub("ISKS200", "Discovery",noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$Coh <- gsub("rep763", "Replication",noC3_df_comb_rnd2_sub$Coh)

##removed Sarcoma geneset; Oct17-2020
noC3_df_comb_rnd2_sub$gene <- factor(x = noC3_df_comb_rnd2_sub$gene,
                            levels = c("Centrosome geneset","Shelterin geneset","TP53"), ordered = TRUE)

library(ggplot2)
# forest_custplot <- function(df){
#   dotCOLS = c("#030000", "#030000")
#   barCOLS = c("#030000", "#030000")
#   xname <- expression(paste(italic("Log"), "OR"))
#   p <- ggplot(df, aes(x=gene, y=log(OR_Fish), ymin=log(CI_lower), ymax=log(CI_upper),col=Coh,fill=Coh)) + 
#     #specify position here
#     geom_linerange(size=1,position=position_dodge(width = 0.6)) +
#     geom_hline(yintercept=0, lty=2) +
#   #  geom_hline(yintercept=1, lty=2) +
#     #specify position here too
#     geom_point(size=4, aes(shape = Coh, color = Coh), position=position_dodge(width = 0.6)) +
# #    geom_point(aes(size=5, shape=21, colour="white", stroke = 0.5,position=position_dodge(width = #0.5)) +
#     scale_fill_manual(values=barCOLS)+
#     scale_color_manual(values=dotCOLS)+
#     scale_x_discrete(name="") + 
#     scale_y_continuous(name="Enrichment in ISKS compared to controls [Log2 Odds ratio]") +
#     coord_flip() +
#     theme_minimal() + theme(legend.position="bottom") + theme(legend.title = element_blank()) +
#     theme(legend.text = element_text(size=8))
#   return(p)
# }


noC3_df_comb_rnd2_sub$Coh <- as.factor(noC3_df_comb_rnd2_sub$Coh)
noC3_df_comb_rnd2_sub$Coh = factor(noC3_df_comb_rnd2_sub$Coh, levels = c("Replication", "Discovery") )


forest_custplot_rep <- function(df){
  g1 = ggplot(df, aes(x = gene, y = log2(OR_Fish), group = Coh) ) +
  #  geom_point(position = position_dodge(width = .75) ) +
    geom_point(size=4, aes(shape = Coh), position=position_dodge(width = 0.6)) + 
    geom_errorbar( aes(ymin = log2(CI_lower), ymax = log2(CI_upper),
                       linetype = Coh,
                       width = c(.1, .1, .1, .1, .1, 0.1) ),
                   position = position_dodge(width = .6) ) +
      theme_bw() + 
      labs(y = "Enrichment in ISKS compared to controls [Log2 Odds ratio]",
           x = "") +
     # geom_rect(xmin = -Inf, xmax = Inf, ymin = -.25, ymax = .25, 
      #      fill = "grey54", alpha = .05) +
      scale_y_continuous(breaks = seq(0, 11, by = 2) ) + 
      coord_flip() +
      scale_linetype_manual(values = c("solid", "solid"),
                            name = element_blank(),
                            labels = c("Replication", "Discovery") ) + 
     scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("Replication", "Discovery") ) 
return(g1)
}

noC3_df_comb_rnd2_sub$Coh = factor(noC3_df_comb_rnd2_sub$Coh, levels = c("Replication", "Discovery") )

g1_rep <- forest_custplot_rep(noC3_df_comb_rnd2_sub)

g2_rep <- g1_rep %+% 
     noC3_df_comb_rnd2_sub +
     scale_linetype_manual(values = c("solid", "solid"),
                           name = element_blank(),
                           labels = c("Replication", "Discovery"),
                           guide = guide_legend(reverse = TRUE) ) + scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("Replication", "Discovery"), guide = guide_legend(reverse = TRUE) )

p_forest_rep <- g2_rep + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank())

p_forest_rep <- p_forest_rep + ggtitle("Replication set C45") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) +  theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(axis.line.x = element_line(color="black", size = 1)) + theme(legend.position = "right") +
  geom_hline(yintercept = 0, lty = 2)

p_forest_rep
#p_forest_rep <- forest_custplot(noC3_df_comb_rnd2_sub) + ggtitle("Replication set C45") + guides(fill=guide_legend(nrow=1,byrow=TRUE)) + scale_shape_manual(values = c(15,21)) + theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(legend.position = "top") + theme(axis.line.x = element_line(color="black", size = 1))
  
#p_forest_rep


##################
##C345 subsetted geneset and cohorts 
##removed Sarcoma geneset; Oct17-2020
df_comb_rnd2_sub <- df_comb_rnd2[df_comb_rnd2$Coh %in% c("ISKS200", "rep763") &
                               df_comb_rnd2$gene %in% c("Shelterin", "CEP_HAUS_core",
                                                        "TP53_control"),]
df_comb_rnd2_sub$Coh <- droplevels(df_comb_rnd2_sub$Coh)
df_comb_rnd2_sub$gene <- droplevels(df_comb_rnd2_sub$gene)
df_comb_rnd2_sub$gene <- gsub("CEP_HAUS_core","Centrosome geneset",df_comb_rnd2_sub$gene)
df_comb_rnd2_sub$gene <- gsub("Shelterin", "Shelterin geneset",df_comb_rnd2_sub$gene)
#df_comb_rnd2_sub$gene <- gsub("SARC_genes", "Sarcoma geneset",df_comb_rnd2_sub$gene)
df_comb_rnd2_sub$gene <- gsub("TP53_control", "TP53",df_comb_rnd2_sub$gene)
write.table(df_comb_rnd2_sub, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/Tables/C345_aug_repset_complex_OR_sub.tsv", sep = "\t", row.names = F, quote = F)

df_comb_rnd2_sub$Coh <- gsub("ISKS200", "Discovery",df_comb_rnd2_sub$Coh)
df_comb_rnd2_sub$Coh <- gsub("rep763", "Replication",df_comb_rnd2_sub$Coh)

df_comb_rnd2_sub$gene <- factor(x = df_comb_rnd2_sub$gene,
                            levels = c("Centrosome geneset","Shelterin geneset", "TP53"), ordered = TRUE)



g1_C345_rep <- forest_custplot_rep(df_comb_rnd2_sub)

df_comb_rnd2_sub$Coh = factor(df_comb_rnd2_sub$Coh, levels = c("Replication", "Discovery") )

g2_C345_rep <- g1_C345_rep %+% 
     df_comb_rnd2_sub +
     scale_linetype_manual(values = c("solid", "solid"),
                           name = element_blank(),
                           labels = c("Replication", "Discovery"),
                           guide = guide_legend(reverse = TRUE) ) + scale_shape_manual(values = c(15,19),
                            name = element_blank(),
                            labels = c("Replication", "Discovery"), guide = guide_legend(reverse = TRUE) )

p_forest_C345 <- g2_C345_rep + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank())

p_forest_C345 <- p_forest_C345 + ggtitle("Replication set C345") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) +  theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(axis.line.x = element_line(color="black", size = 1)) + theme(legend.position = "right") +
  geom_hline(yintercept = 0, lty = 2)

p_forest_C345

#df_comb_rnd2_sub$Coh <- as.factor(df_comb_rnd2_sub$Coh)
#p_forest_C345 <- forest_custplot(df_comb_rnd2_sub) + ggtitle("Replication set C345") + guides(fill=guide_legend(nrow=1,byrow=TRUE)) + scale_shape_manual(values = c(15,21)) + theme(axis.text.y = element_text(face="bold", size=14)) + theme(axis.text.x = element_text(face="bold", size=14)) + theme(axis.title.x = element_text(face = "italic")) + theme(legend.position = "top") + theme(axis.line.x = element_line(color="black", size = 1))
  
# p_forest_C345

```


##multiplot forestplots
```{r echo=FALSE, warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}
source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
multiplot(p_forest, p_forest_CV_345, p_forest_rep, p_forest_C345, cols = 2)
p1 <- p_forest_C345 + ggtitle("") + theme(legend.position = c(0.7,0.5))
p2 <- p_forest_CV_345 + ggtitle("") + theme(legend.position = c(0.7,0.5))
multiplot(p1, p2, cols = 1)
```

##for photoshop manipulation; axis aligned
```{r}
#https://divingintogeneticsandgenomics.rbind.io/post/align-multiple-ggplot2-plots-by-axis/

library(cowplot)
p1 <- p_forest_C345 + ggtitle("") 
p2 <- p_forest_CV_345 + ggtitle("")
pp <- list(p1, p2)
tiff("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Manuscript_docs/aligned_forestplots_300dpi.tiff", units="in", width=5, height=5, res=300)
plot_grid(plotlist=pp, ncol=1, align='v')
dev.off()



```


##AR AD flowchart(variant selection for PID and SKAT)
##C3 variant filter(revisit)
