---
title: "Summary Synonymous"
author: "Swetansu Pattnaik"
date: "31/10/2019"
output: html_document
---

---
title: "Summary_exome_analysis"
author: "Swetansu Pattnaik"
date: "26/09/2019"
output: html_document
---

```{r setup, include=FALSE}
.libPaths(c( "/home/shu/R/x86_64-redhat-linux-gnu-library/3.4", .libPaths() ) )
knitr::opts_chunk$set(echo = TRUE)
```

##Meta analysis of custom geneset

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggrepel)
library(knitr)
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)
library(topGO)
```

```{r echo=FALSE}
##qqplot function SKAT output
gg_qqplot_genes <- function(data, ci = 0.95, genes, SKAT = NULL) {
  
  if(is.null(SKAT)){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol)
    ps <- data$pval_SKATO
  }
  else if(SKAT == "pval_SKATbin"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol)
    ps <- data$pval_SKATbin
  }
  else if(SKAT == "pval_SKAT"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol)
    ps <- data$pval_SKAT
  }
  # all_genes <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
  n  <- length(ps)
  df <- data.frame(
    observed = -log10(sort(ps)),
    expected = -log10(ppoints(n)),
    #expected = -log10(sort(pe)),
    clower   = -log10(qbeta(p = (1 - ci) / 2, shape1 = 1:n, shape2 = n:1)),
    cupper   = -log10(qbeta(p = (1 + ci) / 2, shape1 = 1:n, shape2 = n:1)),
    gene_ID  = gene_ID
  )
  log10Pe <- expression(paste("Expected -log"[10], plain(P)))
  log10Po <- expression(paste("Observed -log"[10], plain(P)))
  
  genes_all <- c(genes, gene_top)
  df <- mutate(df, sel=ifelse(df$gene_ID %in% genes_all, 1, 0))
  ptest = ggplot(df, aes(expected, observed)) +
    geom_point(aes(col=as.factor(sel))) +
    scale_color_manual(values=c( "black", "red"))
  ptest = ptest + geom_text_repel(data=filter(df, sel > 0), aes(label=gene_ID), colour = "red", size = 3.5,
                                  box.padding = unit(0.35, "lines"),
                                  point.padding = unit(0.3, "lines"))
  ptest + geom_abline(intercept = 0, slope = 1, alpha = 0.5) +
    geom_line(aes(expected, cupper), linetype = 2) +
    geom_line(aes(expected, clower), linetype = 2) +
    xlab(log10Pe) +
    ylab(log10Po) + theme(legend.position="none")
}

source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")

```

**Filter Thresholds** <br />
1. VAF >= 0.25 <br />
2. intra cohort_MAF filter <= 3/(2*Number in cohort) <br />
3. gnomad_AF_NFE <= 0.005 <br />

**Scoring/Weighting** <br />

 <br />


```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}

Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Syn/Exome_skat_filt3_nCH_C5eqC4_nonmds_iskrisc_05Sept_rect_ASP_syn.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
#Exome_pc123_srt_SKATO1 <- lapply(df_skat, function(x) x[order(x$pval_SKATO, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})

SKAT_plots_eigen <- lapply(Exome_pc123_srt_SKAT, function(x)gg_qqplot_genes(data = x, ci = 0.95, genes = x[,1], SKAT = "pval_SKATbin"))
main_lab <- c("No Adjustment", "PC123", "Gender", "Gender_PC123")
names(SKAT_plots_eigen) <- main_lab
SKAT_plots_eigen <- lapply(names(SKAT_plots_eigen), function(x) SKAT_plots_eigen[[x]] + ggtitle(x) + theme(plot.title = element_text(size = 8, face = "bold")))
multiplot(plotlist = SKAT_plots_eigen, cols = 2)

```

##Enrichment of positive correlations to phenotype

```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Syn/Exome_skat_filt3_nCH_C5eqC4_nonmds_iskrisc_05Sept_rect_ASP_syn.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})
Exome_pc123_srt_SKAT_case_enr_nCH <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Syn/Exome_pc123_srt_SKAT_case_enr_nCH_iskrisc_05Sept_rect_ASP_cmaf_syn.rds")
##Add p-value
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- Map(cbind.data.frame, Exome_pc123_srt_SKAT_case_enr_nCH, Exome_pc123_srt_SKAT)

##Remove genes that have SKATbin_pval >= 0.1, this selects only significant genes for the PPI enrichment
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
  x[x$pval_SKATbin < 0.1 & x$wt_diff > 0,])

#Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
#  x[x$pval_SKATbin < 0.2 & x$wt_diff > 0,])

##Better option for Enriched list: sort by -log(p_val) * weight difference ; appropriately factors influence of variant on ISKS phenotype

Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, 
                                                  function(x) cbind.data.frame(x, "rank_score" = -log10(x[,9]) * x[,6])) ##added intra cohort MAF filtered variant positions
                                                    
Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_ranked, function(x)
  x[order(x[,12], decreasing = T),]) ##added intra cohort MAF filtered variant positions


```


##Use PPI approach to derive differential enrichment of mutated interactomes in ISKS and RISC(15) combined.
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
##get graph degree from the genes in the top 1000 enriched list
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)


get_topSKAT_degree <- function(enr_df){

skat_genes_top100 <- as.character(enr_df[,3])

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
#can_net <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Biogrid_latest/Biog_net_hs.sif", header = T, sep = "\t", stringsAsFactor = F)
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% skat_genes_top100 
                               & as.character(can_net1$to) %in% skat_genes_top100, ])
uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)



ret_df <- as.data.frame(igraph::degree(uniongraph))
ret_df$gene <- rownames(ret_df)
colnames(ret_df)[1] <- c("degree")

l1 <- lapply(ret_df[,2], function(x)as_ids(adjacent_vertices(uniongraph, v = x)[[1]]))
l2 <- lapply(l1, function(x)paste(x, sep=",", collapse=","))
ret_df$interactors <- unlist(l2)

return(ret_df)
}


##Fisher exact test for enrichment of subgraph related to each protein
#gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]][,1:1000]
gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]]

df_degree <- get_topSKAT_degree(gender_PC123_cont_df)
gender_PC123_cont_df$degree <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 1]
gender_PC123_cont_df$int <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 3]
gender_PC123_cont_df$degree <- ifelse(is.na(gender_PC123_cont_df$degree), 0, gender_PC123_cont_df$degree)
gender_PC123_cont_df$rank_PPI <- gender_PC123_cont_df$rank_score * log(gender_PC123_cont_df$degree + 2)
gender_PC123_cont_df <- gender_PC123_cont_df[order(gender_PC123_cont_df$rank_PPI, decreasing = T),]
###latest fisher test based on degrees in biogrid versus enriched graphs

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
top_genes_enr <- as.character(gender_PC123_cont_df$gene)
para_fisher_fun_new <- function(gene_sym){
  gene_sym <- gene_sym[3]
  print(gene_sym)
  can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
  can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
  can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes_enr 
                                 & as.character(can_net1$to) %in% top_genes_enr, ])
  uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  ##degree biogrid
  deg_biog <- igraph::degree(can_net_graph1)[which(names(igraph::degree(can_net_graph1)) %in% gene_sym)]
  deg_union <- igraph::degree(uniongraph)[which(names(igraph::degree(uniongraph)) %in% gene_sym)]
  #tot_biog <- igraph::vcount(can_net_graph1) ##should be edge count not vertex count
  #tot_union <- igraph::vcount(uniongraph)
  tot_biog <- igraph::ecount(can_net_graph1) 
  tot_union <- igraph::ecount(uniongraph)
  
  ##test
  inp <- c(deg_union, deg_biog, tot_union, tot_biog)
  mgrb_tsg <- matrix(inp ,nrow = 2, ncol = 2)
  colnames(mgrb_tsg) <- c("deg_enr", "deg_bio")
  rownames(mgrb_tsg) <- c("Enriched", "Biog")
  #ft <- fisher.test(mgrb_tsg, alternative = "greater")
  ft <- fisher.test(mgrb_tsg)
  ft_df <- cbind.data.frame("gene" =  gene_sym, "PPI_p_val_wt" = ft$p.value,
                            "CI_lower" = ft$conf.int[1],
                            "CI_upper" = ft$conf.int[2],
                            "OR" = ft$estimate)
  
  return(ft_df)
}



library(parallel)
cl <- makeCluster(25)
#para_pheno <- parLapply(cl, 1:nrow(IBD_dist1), function(i) pick_pinf(IBD_dist1[i,]))
clusterExport(cl, c("can_net", "top_genes_enr", "para_fisher_fun_new"))
system.time(para_fish <- parApply(cl, gender_PC123_cont_df, 1, para_fisher_fun_new))
stopCluster(cl)
fisher_res <- do.call("rbind.data.frame",para_fish)
ppi_res_fil_final <- cbind.data.frame(gender_PC123_cont_df, fisher_res)

```

##Cliques in the enriched set of genes
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
######Cliques in uniongraph (enriched cliques from SKAT)
top_genes <- as.character(gender_PC123_cont_df$gene)
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes 
                               & as.character(can_net1$to) %in% top_genes, ])

uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)

te1 <- cliques(uniongraph, min=3)
cpx <- names(unlist(te1))
cpx_np_all <- unique(can_net1[as.character(can_net1$from) %in% cpx 
                               & as.character(can_net1$to) %in% cpx, ])
cpx_graph <- igraph::graph.data.frame(cpx_np_all, directed = F)

net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
net_new_t_list <- network(net_mat_t_list, directed = FALSE)
network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
gnet <- ggnet2(net_new_t_list, alpha = 0.75, edge.alpha = 0.5, label = TRUE, label.size = 3,  mode = "kamadakawai") + theme(legend.position = "bottom") + theme(legend.title = element_blank())
  
  gnet

```

