---
title: "Summary_exome_analysis"
author: "Swetansu Pattnaik"
date: "02/05/2021"
output: html_document
---

```{r setup, include=FALSE}
#.libPaths(c( "/home/shu/R/x86_64-redhat-linux-gnu-library/3.4", .libPaths() ) )
knitr::opts_chunk$set(echo = TRUE)
```

##Meta analysis of custom geneset

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggrepel)
library(knitr)
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)
library(topGO)
```

```{r echo=FALSE}
##qqplot function SKAT output
gg_qqplot_genes <- function(data, ci = 0.95, genes, SKAT = NULL) {
  
  if(is.null(SKAT)){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATO, decreasing = F),]$symbol)
    ps <- data$pval_SKATO
  }
  else if(SKAT == "pval_SKATbin"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKATbin, decreasing = F),]$symbol)
    ps <- data$pval_SKATbin
  }
  else if(SKAT == "pval_SKAT"){
    data$symbol <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
    gene_top <- head(as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol), 10)
    gene_ID <- as.character(data[order(data$pval_SKAT, decreasing = F),]$symbol)
    ps <- data$pval_SKAT
  }
  # all_genes <- ifelse(is.na(data$symbol), as.character(data$eg_ID) , as.character(data$symbol) )
  n  <- length(ps)
  df <- data.frame(
    observed = -log10(sort(ps)),
    expected = -log10(ppoints(n)),
    #expected = -log10(sort(pe)),
    clower   = -log10(qbeta(p = (1 - ci) / 2, shape1 = 1:n, shape2 = n:1)),
    cupper   = -log10(qbeta(p = (1 + ci) / 2, shape1 = 1:n, shape2 = n:1)),
    gene_ID  = gene_ID
  )
  log10Pe <- expression(paste("Expected -log"[10], plain(P)))
  log10Po <- expression(paste("Observed -log"[10], plain(P)))
  
  genes_all <- c(genes, gene_top)
  df <- mutate(df, sel=ifelse(df$gene_ID %in% genes_all, 1, 0))
  ptest = ggplot(df, aes(expected, observed)) +
    geom_point(aes(col=as.factor(sel))) +
    scale_color_manual(values=c( "black", "red"))
  ptest = ptest + geom_text_repel(data=filter(df, sel > 0), aes(label=gene_ID), colour = "red", size = 3.5,
                                  box.padding = unit(0.35, "lines"),
                                  point.padding = unit(0.3, "lines"))
  ptest + geom_abline(intercept = 0, slope = 1, alpha = 0.5) +
    geom_line(aes(expected, cupper), linetype = 2) +
    geom_line(aes(expected, clower), linetype = 2) +
    xlab(log10Pe) +
    ylab(log10Po) + theme(legend.position="none")
}

source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")

```

**Filter Thresholds** <br />
1. VAF >= 0.35 <br />
2. Eigenphred/Comb_score >= 3 <br />
2. intra cohort_MAF filter <= 3/(2*Number in cohort) <br />
3. gnomad_AF_NFE <= 0.005 <br />

**Scoring/Weighting** <br />
EigenPhred scale scoring was introduced manually for the following variants:<br />
C3 = EigenPhredscore <br />
C4 = 45 <br />
ClinVar (*Pathogenic/likely Pathogenic*) C5 = 45 <br />
C3/C4 Variants in the last 5 percent of the C-terminal region of the protein = assigned score/2 <br />


```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}

Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/Exome_skat_para_result_CVD_combset2020_uni_MAF_PC1234_ver4.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
#Exome_pc123_srt_SKATO1 <- lapply(df_skat, function(x) x[order(x$pval_SKATO, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})

SKAT_plots_eigen <- lapply(Exome_pc123_srt_SKAT, function(x)gg_qqplot_genes(data = x, ci = 0.95, genes = as.character(x[,1]), SKAT = "pval_SKATbin"))
main_lab <- c("No Adjustment", "PC1234", "Gender", "Gender_PC1234")
names(SKAT_plots_eigen) <- main_lab
SKAT_plots_eigen <- lapply(names(SKAT_plots_eigen), function(x) SKAT_plots_eigen[[x]] + ggtitle(x) + theme(plot.title = element_text(size = 8, face = "bold")))
multiplot(plotlist = SKAT_plots_eigen, cols = 2)

```


```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/Exome_skat_para_result_CVD_combset2020_uni_MAF_PC1234_ver4.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})
Exome_pc123_srt_SKAT_case_enr_nCH <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/Exome_para_pc123_SKAT_Enriched_CVD_2021.rds")
##Add p-value
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- Map(cbind.data.frame, Exome_pc123_srt_SKAT_case_enr_nCH, Exome_pc123_srt_SKAT)

##save for volcano_plot
#write.table(Exome_pc123_srt_SKAT_case_enr_nCH_pval[[4]], "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Sep05_rect_ASP_graph_final_cmaf_new_score_volcano.tsv", sep = "\t", row.names = F, quote = F)

##Remove genes that have SKATbin_pval >= 0.1, this selects only significant genes for the PPI enrichment
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
  x[x$pval_SKATbin < 0.1 & x$wt_diff > 0,])
##use SKATO output
#Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
#  x[x$pval_SKATO < 0.1 & x$wt_diff > 0,])

#Exome_pc123_srt_SKAT_case_enr_nCH_pval <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, function(x)
#  x[x$pval_SKATbin < 0.2 & x$wt_diff > 0,])

##Better option for Enriched list: sort by -log(p_val) * weight difference ; appropriately factors influence of variant on ISKS phenotype
##use SKATbin p-value
Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_pval, 
                                                  function(x) cbind.data.frame(x, "rank_score" = -log10(x[,14]) * x[,6])) 
                                                    
Exome_pc123_srt_SKAT_case_enr_nCH_ranked <- lapply(Exome_pc123_srt_SKAT_case_enr_nCH_ranked, function(x)
  x[order(x[,17], decreasing = T),]) ##added intra cohort MAF filtered variant positions

##get variant tab
pc123_gender_tab_top1000 <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]]
# fil_tab_noCH <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/all_asrb_mgrb_skatinp_combset2020_clin_C3C4C5_NFE0002_AD_all_fields_rnd3.tsv", sep = "\t", header = T, stringsAsFactors = F)
# pc123_gender_tab_top1000_VAR <- fil_tab_noCH[fil_tab_noCH$gene_symbol %in% pc123_gender_tab_top1000$gene & fil_tab_noCH$comb_score >= 5.6 & fil_tab_noCH$VAF >= 0.35,]
# pc123_gender_tab_top1000_VAR <- pc123_gender_tab_top1000_VAR[pc123_gender_tab_top1000_VAR$VARIANT %in% unlist(strsplit(as.character(pc123_gender_tab_top1000$maf_filt_var), split = ",")),]
# pc123_gender_tab_top1000_VAR$gene_Pval <- pc123_gender_tab_top1000[match(pc123_gender_tab_top1000_VAR$gene_symbol, pc123_gender_tab_top1000$gene),15] ##SKATO
# #head(pc123_gender_tab_top1000_VAR[,c(1:6,8:9,11,15,17:18,20,23:25,30,53,57,59:68,72,119:121)])
# pc123_gender_tab_top1000_VAR <- pc123_gender_tab_top1000_VAR[,c(1:6,8:9,11,15,17:18,20,23:25,30,53,57,59:68,72,125:132)]
# pc123_gender_tab_top1000_VAR <- unique(pc123_gender_tab_top1000_VAR)
# write.table(pc123_gender_tab_top1000_VAR, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/Exome_Enriched_pc_gender_controlled_top_geneVARIANTS_CAIRNS_pval01.tsv", sep = "\t", row.names = F, quote = F)
#write.table(pc123_gender_tab_top1000_VAR, "/home/shu/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/discovery_set/round2/Exome_Enriched_pc_gender_controlled_top_geneVARIANTS_sep05_ASP_cmaf02_new_score_rnd2.tsv",sep = "\t", row.names = F, quote = F)

```


##Use PPI approach to derive differential enrichment of mutated interactomes in CVD dataset.
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
##get graph degree from the genes in the top 1000 enriched list
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)


get_topSKAT_degree <- function(enr_df){

skat_genes_top100 <- as.character(enr_df[,3])

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
#can_net <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/Biogrid_latest/Biog_net_hs.sif", header = T, sep = "\t", stringsAsFactor = F)
can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% skat_genes_top100 
                               & as.character(can_net1$to) %in% skat_genes_top100, ])
uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)



ret_df <- as.data.frame(igraph::degree(uniongraph))
ret_df$gene <- rownames(ret_df)
colnames(ret_df)[1] <- c("degree")

l1 <- lapply(ret_df[,2], function(x)as_ids(adjacent_vertices(uniongraph, v = x)[[1]]))
l2 <- lapply(l1, function(x)paste(x, sep=",", collapse=","))
ret_df$interactors <- unlist(l2)

return(ret_df)
}


##Fisher exact test for enrichment of subgraph related to each protein
#gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]][,1:1000]
gender_PC123_cont_df <- Exome_pc123_srt_SKAT_case_enr_nCH_ranked[[4]]

df_degree <- get_topSKAT_degree(gender_PC123_cont_df)
gender_PC123_cont_df$degree <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 1]
gender_PC123_cont_df$int <- df_degree[match(gender_PC123_cont_df$gene, df_degree$gene), 3]
gender_PC123_cont_df$degree <- ifelse(is.na(gender_PC123_cont_df$degree), 0, gender_PC123_cont_df$degree)
gender_PC123_cont_df$rank_PPI <- gender_PC123_cont_df$rank_score * log(gender_PC123_cont_df$degree + 2)
gender_PC123_cont_df <- gender_PC123_cont_df[order(gender_PC123_cont_df$rank_PPI, decreasing = T),]
###latest fisher test based on degrees in biogrid versus enriched graphs

can_net <- read.delim("~/VDLab_scripts/BioGrid/biogrid_db_all_subnet.sif", header = T, sep = " ", stringsAsFactor = F)
top_genes_enr <- as.character(gender_PC123_cont_df$gene)

para_fisher_fun_new <- function(gene_sym){
  gene_sym <- gene_sym[3]
  print(gene_sym)
  can_net_graph <- igraph::graph.data.frame(can_net, directed = F)
  can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
  can_net1 <- igraph::as_data_frame(can_net_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes_enr 
                                 & as.character(can_net1$to) %in% top_genes_enr, ])
  uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  ##degree biogrid
  deg_biog <- igraph::degree(can_net_graph1)[which(names(igraph::degree(can_net_graph1)) %in% gene_sym)]
  deg_union <- igraph::degree(uniongraph)[which(names(igraph::degree(uniongraph)) %in% gene_sym)]
  #tot_biog <- igraph::vcount(can_net_graph1) ##should be edge count not vertex count
  #tot_union <- igraph::vcount(uniongraph)
  tot_biog <- igraph::ecount(can_net_graph1) 
  tot_union <- igraph::ecount(uniongraph)
  
  ##test
  #inp <- c(deg_union, deg_biog, tot_union - deg_union, tot_biog - deg_biog)
  inp <- c(deg_union, deg_biog, tot_union, tot_biog)
  mgrb_tsg <- matrix(inp ,nrow = 2, ncol = 2)
  colnames(mgrb_tsg) <- c("deg_enr", "deg_bio")
  rownames(mgrb_tsg) <- c("Enriched", "Biog")
  #ft <- fisher.test(mgrb_tsg, alternative = "greater")
  ft <- fisher.test(mgrb_tsg, conf.int = T, conf.level = 0.95)
  ft_df <- cbind.data.frame("gene" =  gene_sym, "PPI_p_val_wt" = ft$p.value,
                            "CI_lower" = ft$conf.int[1],
                            "CI_upper" = ft$conf.int[2],
                            "OR" = ft$estimate)
  
  return(ft_df)
}



library(parallel)
cl <- makeCluster(25)
#para_pheno <- parLapply(cl, 1:nrow(IBD_dist1), function(i) pick_pinf(IBD_dist1[i,]))
clusterExport(cl, c("can_net", "top_genes_enr", "para_fisher_fun_new"))
system.time(para_fish <- parApply(cl, gender_PC123_cont_df, 1, para_fisher_fun_new))
stopCluster(cl)
fisher_res <- do.call("rbind.data.frame",para_fish)
ppi_res_fil_final <- cbind.data.frame(gender_PC123_cont_df, fisher_res)
write.table(ppi_res_fil_final, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/ppi_res_fil_final_CVD.tsv", sep = "\t", row.names = F, quote = F)
```


```{r}
##Add Fisher's test values to ppi_res_fil_final.tsv


para_fisher_weighted_new <- function(gene_sym){
 
  gene_sym <- gene_sym[3]
  
  ppi_res <- ppi_res_fil_final[ppi_res_fil_final$gene %in% gene_sym,]
  
  ##simple Fisher test
  #inp <- c(deg_union, deg_biog, tot_union - deg_union, tot_biog - deg_biog)
  inp <- c(ppi_res[,1], 117 - ppi_res[,1] , ppi_res[,2], 3205 - ppi_res[,2])
  sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
  colnames(sim_mat) <- c("isks_enr", "mgrb_enr")
  rownames(sim_mat) <- c("hits", "no_hits")
  #ft <- fisher.test(mgrb_tsg, alternative = "greater")
  ft <- fisher.test(sim_mat, alternative = "greater")
  ##Weighted Fisher
  inp1 <- c(ppi_res[,4], 117 - ppi_res[,1] , ppi_res[,5], 3205 - ppi_res[,2])
  sim_mat1 <- matrix(inp1 ,nrow = 2, ncol = 2)
  colnames(sim_mat1) <- c("isks_wt", "mgrb_wt")
  rownames(sim_mat1) <- c("hits", "no_hits")
  ft1 <- fisher.test(sim_mat1, alternative = "greater")
  
  ft_df <- cbind.data.frame("gene" =  gene_sym, "Fish_pval" = ft$p.value,
                            "OR_Fish" = ft$estimate, "Wt_Fish_pval" = ft1$p.value,
                            "Wt_Fish_OR" = ft1$estimate)
  
  return(ft_df)
}



library(parallel)
cl <- makeCluster(25)
#para_pheno <- parLapply(cl, 1:nrow(IBD_dist1), function(i) pick_pinf(IBD_dist1[i,]))
clusterExport(cl, c("ppi_res_fil_final", "para_fisher_weighted_new"))
system.time(para_fish_wt <- parApply(cl, ppi_res_fil_final, 1, para_fisher_weighted_new))
stopCluster(cl)
wt_fisher_res <- do.call("rbind.data.frame",para_fish_wt)
ppi_res_fil_final <- cbind.data.frame(ppi_res_fil_final, wt_fisher_res)
ppi_res_fil_final <- ppi_res_fil_final[,c(1:16,26:30,17:25)]
write.table(ppi_res_fil_final, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/ppi_res_fil_final_CVD_SKATbin_wt_fisher.tsv", sep = "\t", row.names = F, quote = F)


```

##Cliques in the enriched set of genes
```{r, out.width='\\textwidth', fig.height = 7, fig.align='center', echo=FALSE}
######Cliques in uniongraph (enriched cliques from SKAT)
ppi_res_fil_final <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/ppi_res_fil_final_CVD_SKATbin_wt_fisher.tsv", sep = "\t", header = T, stringsAsFactors = F)
ppi_res_fil_final <- ppi_res_fil_final[ppi_res_fil_final$CVD > 1,]
##need biogrid + stringdb for clique detection
strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")

can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")

top_genes <- as.character(ppi_res_fil_final$gene)
can_net_graph <- igraph::graph.data.frame(can_net1, directed = F)
can_net_graph1 <- igraph::simplify(can_net_graph, remove.loops=T, remove.multiple = T)
can_net12 <- igraph::as_data_frame(can_net_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net12$from) %in% top_genes 
                               & as.character(can_net12$to) %in% top_genes, ])

uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)

te1 <- cliques(uniongraph, min=3)
cpx <- names(unlist(te1))
cpx_np_all <- unique(can_net12[as.character(can_net1$from) %in% cpx 
                               & as.character(can_net1$to) %in% cpx, ])
cpx_graph <- igraph::graph.data.frame(cpx_np_all, directed = F)
cpx_graph <- igraph::simplify(cpx_graph, remove.loops=T, remove.multiple = T)
net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
net_new_t_list <- network(net_mat_t_list, directed = FALSE)
network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
gnet <- ggnet2(net_new_t_list, alpha = 0.75, edge.alpha = 0.5, label = TRUE, label.size = 3,  mode = "kamadakawai") + theme(legend.position = "bottom") + theme(legend.title = element_blank())
  
  gnet

```

##GO enrichment of all proteins compared to clique proteins
```{r}
library(enrichR)

dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")

##All proteins
ppi_res_fil_final <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/ppi_res_fil_final_CVD_SKATbin_wt_fisher.tsv", sep = "\t", header = T, stringsAsFactors = F)
ppi_res_fil_final <- ppi_res_fil_final[ppi_res_fil_final$CVD > 1,]

enriched_ppi <- enrichr(ppi_res_fil_final$gene, dbs)
enrichr_df_ppi <- cbind.data.frame("gene_hub" =  "CVD", "GO_MF" = enriched_ppi[[1]]$Term[1:20],
                                       "GO_MF_p_val" = enriched_ppi[[1]]$P.value[1:20],
                                       "GO_CC" = enriched_ppi[[2]]$Term[1:20],
                                       "GO_CC_p_val" = enriched_ppi[[2]]$P.value[1:20],
                                       "GO_BP" = enriched_ppi[[3]]$Term[1:20],
                                       "GO_BP_p_val" = enriched_ppi[[3]]$P.value[1:20])
View(enrichr_df_ppi[,6:7])

##map GO term to gene symbol
xx <- as.list(org.Hs.egGO2EG)
t1 <- unlist(xx["GO:0007512"])
symbols <- mapIds(org.Hs.eg.db, keys = t1, keytype = "ENTREZID", column="SYMBOL")
ppi_res_fil_final$gene[ppi_res_fil_final$gene %in% symbols]
ppi_res_fil_final[ppi_res_fil_final$gene %in% symbols,]
#filter = 'go_id', 


##clique proteins
te3 <- cliques(uniongraph, min=3)
te3_prot <- unique(unlist(lapply(te3, function(x)names(x))))
enriched_te3 <- enrichr(te3_prot, dbs)
enrichr_df_te3 <- cbind.data.frame("gene_hub" =  "CVD", "GO_MF" = enriched_te3[[1]]$Term[1:20],
                                       "GO_MF_p_val" = enriched_te3[[1]]$P.value[1:20],
                                       "GO_CC" = enriched_te3[[2]]$Term[1:20],
                                       "GO_CC_p_val" = enriched_te3[[2]]$P.value[1:20],
                                       "GO_BP" = enriched_te3[[3]]$Term[1:20],
                                       "GO_BP_p_val" = enriched_te3[[3]]$P.value[1:20])
View(enrichr_df_te3[,6:7])

##connected component proteins
groups <- igraph::components(uniongraph)
group_tab <- as.data.frame(groups$membership)
group_tab$genes <- names(groups$membership)

enriched_cc <- enrichr(group_tab$genes, dbs)
enrichr_df_cc <- cbind.data.frame("gene_hub" =  "CVD", "GO_MF" = enriched_cc[[1]]$Term[1:20],
                                       "GO_MF_p_val" = enriched_cc[[1]]$P.value[1:20],
                                       "GO_CC" = enriched_cc[[2]]$Term[1:20],
                                       "GO_CC_p_val" = enriched_cc[[2]]$P.value[1:20],
                                       "GO_BP" = enriched_cc[[3]]$Term[1:20],
                                       "GO_BP_p_val" = enriched_cc[[3]]$P.value[1:20])
View(enrichr_df_cc[,6:7])

```


##Weighted gene set enrichment
##https://cran.r-project.org/web/packages/enrichR/vignettes/enrichR.html
##install from github
```{r}

##Do not run this chunk
library(enrichR)
# dbs <- listEnrichrDbs()
# if (is.null(dbs)) websiteLive <- FALSE
# if (websiteLive) head(dbs)

#dbs <- listEnrichrDbs()

dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")
#if (websiteLive) enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
#enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
##loop over the interactors of each protein and report the top pathway and p-value

#gender_PC123_cont_df from line 285
enrichr_fun <- function(gene_sym, fil_graph){
  enrichr_df <- list()
  for(i in 1:length(gene_sym)){
    print(i)
  fil_genes <- fil_graph[grep(paste("^", as.character(gene_sym[i]), "$", sep = ""), fil_graph$gene),]
  if(fil_genes$degree == 0){ 
    enrichr_df[[i]] <- NULL 
    }
  else{
prot <- c(as.character(gene_sym[i]), unlist(strsplit(fil_genes$int, split = ",")))
dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")
enriched <- enrichr(prot, dbs)
print(length(enriched))
   enrichr_df[[i]] <- cbind.data.frame("gene_hub" =  gene_sym[i], "GO_MF" = enriched[[1]]$Term[1],
                                       "GO_MF_p_val" = enriched[[1]]$P.value[1],
                                       "GO_CC" = enriched[[2]]$Term[1],
                                       "GO_CC_p_val" = enriched[[2]]$P.value[1],
                                       "GO_BP" = enriched[[3]]$Term[1],
                                       "GO_BP_p_val" = enriched[[3]]$P.value[1])
  
  }
  
  }
  return(enrichr_df)
}

ppi_res_fil_final <- ppi_res_fil_final[!is.na(ppi_res_fil_final$gene),]
goNet_enrich <- enrichr_fun(ppi_res_fil_final$gene, ppi_res_fil_final)
goNet_enrich_res <- do.call("rbind.data.frame",goNet_enrich)
saveRDS(goNet_enrich_res, file = "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/goNet_enrich_res_sep05_combset2020_CVD.rds", compress = T)

#goNet_enrich_res <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/EPIT/round2/goNet_enrich_res_sep05_combset2020_EPIT.rds")

fil_graph_final_comb_GO <- ppi_res_fil_final

fil_graph_final_comb_GO[,c(31:36)] <- goNet_enrich_res[match(fil_graph_final_comb_GO$gene, goNet_enrich_res$gene_hub),c(2:7)]

##combine p-values: Fisher's method (basic)
# comb_fisher <- function(p_val_vec){
#   c_pval <- pchisq(sum(log(p_val_vec)*-2), df = 2*length(p_val_vec), lower.tail = F)
#   return(c_pval)
# }

fil_graph_final_comb_GO <- fil_graph_final_comb_GO[,c(1:10,14,18:25,27,30:36)]
#inp_pval <- fil_graph_final_comb_GO[,c(12,17)]
#fil_graph_final_comb_GO$comb_pval <- apply(inp_pval, 1, comb_fisher)
write.table(fil_graph_final_comb_GO, file = "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CVD_DIANE/round2/CVD_AR_AD/SKAT/CVD_combset2021_final_PPI_comb_GO.tsv", sep = "\t", row.names = F, quote = F)

```



