---
title: "ASRB_cliques"
author: "Swetansu Pattnaik"
date: "15/04/2021"
output: html_document
---

```{r setup, include=FALSE}
`%nin%` = Negate(`%in%`)
knitr::opts_chunk$set(echo = TRUE)
```

##load libraries
```{r echo = FALSE, warning = FALSE, message = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}
library(readxl)
library(ggplot2)
library(ggdendro)
library(dendextend)
library(dplyr)
library(ggrepel)
library(knitr)
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)
library(topGO)
```


##Clique detection (cliq_OR_SKAT.R and SKATOPINT_package.Rmd; line:701-711)
##Select ASRB genes without controlling for age
```{r}
Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Exome_skat_para_result_CAIRNS_combset2020_uni_MAF_PC1234_ver4.rds")

df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})
Exome_pc123_srt_SKAT_case_enr_nCH <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Exome_para_pc123_SKAT_Enriched_CAIRNS_2020.rds")
##Add p-value
Exome_pc123_srt_SKAT_case_enr_nCH_pval <- Map(cbind.data.frame, Exome_pc123_srt_SKAT_case_enr_nCH, Exome_pc123_srt_SKAT)

cairns_mgrb_genes <- Exome_pc123_srt_SKAT_case_enr_nCH_pval[[4]]
cairns_mgrb_genes_top <- cairns_mgrb_genes[cairns_mgrb_genes$wt_diff > 0 & cairns_mgrb_genes$pval_SKATbin < 0.1,]

filt1_df <- cairns_mgrb_genes_top[cairns_mgrb_genes_top$CAIRNS > 1 & cairns_mgrb_genes_top$MGRB <= 14,]
top_genes <- as.character(filt1_df$gene)
##filter3 : based on hypergeometric score of PPI (can be used for further fine-tuning and ranking)
##not needed for gene selection


strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")

can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% top_genes 
                               & as.character(can_net1$to) %in% top_genes, ])
# prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cep_genes 
#                                & as.character(can_net1$to) %in% cep_genes, ])

uniongraph <- igraph::graph.data.frame(prot_np_all, directed = F)

te3 <- max_cliques(uniongraph, min=3)
names(te3) <- paste("c", 1:length(te3), sep = "_")

##OR use a more generic connected component based filter
groups <- components(uniongraph)
group_tab <- as.data.frame(groups$membership)
group_tab$genes <- names(groups$membership)
#saveRDS(te3, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/Cliques_max101.rds", compress = T)
#saveRDS(te3, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Cliques/Cliques_min4.rds", compress = T)

```

##GO analysis
```{r}
library(enrichR)
# dbs <- listEnrichrDbs()
# if (is.null(dbs)) websiteLive <- FALSE
# if (websiteLive) head(dbs)

#dbs <- listEnrichrDbs()

dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")
#if (websiteLive) enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
#enriched <- enrichr(c("Runx1", "Gfi1", "Gfi1b", "Spi1", "Gata1", "Kdr"), dbs)
##loop over the interactors of each protein and report the top pathway and p-value



##clique proteins
te3_prot <- unique(unlist(lapply(te3, function(x)names(x))))
enriched_te3 <- enrichr(te3_prot, dbs)
enrichr_df_te3 <- cbind.data.frame("gene_hub" =  "ASRB", "GO_MF" = enriched_te3[[1]]$Term[1:20],
                                       "GO_MF_p_val" = enriched_te3[[1]]$P.value[1:20],
                                       "GO_CC" = enriched_te3[[2]]$Term[1:20],
                                       "GO_CC_p_val" = enriched_te3[[2]]$P.value[1:20],
                                       "GO_BP" = enriched_te3[[3]]$Term[1:20],
                                       "GO_BP_p_val" = enriched_te3[[3]]$P.value[1:20])
View(enrichr_df_te3[,6:7])
##connected component proteins
##next version: threshold based on size of connected component
#group_tab_cc_filt <- group_tab[as.character(group_tab$`groups$membership`) %in% names(which(table(group_tab$`groups$membership`) > 2)), ]
enriched_cc <- enrichr(group_tab$genes, dbs)
enrichr_df_cc <- cbind.data.frame("gene_hub" =  "ASRB", "GO_MF" = enriched_cc[[1]]$Term[1:20],
                                       "GO_MF_p_val" = enriched_cc[[1]]$P.value[1:20],
                                       "GO_CC" = enriched_cc[[2]]$Term[1:20],
                                       "GO_CC_p_val" = enriched_cc[[2]]$P.value[1:20],
                                       "GO_BP" = enriched_cc[[3]]$Term[1:20],
                                       "GO_BP_p_val" = enriched_cc[[3]]$P.value[1:20])
View(enrichr_df_cc[,6:7])
##All SKAT genes
enriched_skat <- enrichr(as.character(filt1_df$gene), dbs)
enrichr_df_skat <- cbind.data.frame("gene_hub" =  "ASRB", "GO_MF" = enriched_skat[[1]]$Term[1:20],
                                  "GO_MF_p_val" = enriched_skat[[1]]$P.value[1:20],
                                  "GO_skat" = enriched_skat[[2]]$Term[1:20],
                                  "GO_skat_p_val" = enriched_skat[[2]]$P.value[1:20],
                                  "GO_BP" = enriched_skat[[3]]$Term[1:20],
                                  "GO_BP_p_val" = enriched_skat[[3]]$P.value[1:20])
View(enrichr_df_skat[,6:7])
##next version: add page rank based eigen ranking to nodes

```


##Map GO IDs to gene symbols
```{r}
##map GO term to gene symbol
xx <- as.list(org.Hs.egGO2EG)

df_skat_GO <- enrichr_df_skat$GO_BP
df_skat_GO <- gsub("^*.*\\(", "", df_skat_GO)
df_skat_GO <- gsub("\\)", "", df_skat_GO)
t1 <- lapply(df_skat_GO, function(y)unlist(xx[y]))
#symbols <- mapIds(org.Hs.eg.db, keys = t1, keytype = "ENTREZID", column="SYMBOL")
t1_symbols <- lapply(t1, function(x)tryCatch(mapIds(org.Hs.eg.db, keys = x, keytype = "ENTREZID", column="SYMBOL"), error=function(x) NULL))

t1_symbols_match <- lapply(t1_symbols, function(x)unique(x[x %in% as.character(filt1_df$gene)]))
t1_symbols_match <- lapply(t1_symbols_match, function(x)paste(x,collapse=","))

```

##Map genes to gene functions

```{r}
##Gene function summary
library(mygene)
# gene <- getGene("1017", fields="all")
# gene$summary
#t1 <- te3_prot
##Clique proteins
EGID <- as.data.frame(mapIds(org.Hs.eg.db, keys = te3_prot, keytype = "SYMBOL", column="ENTREZID"))
EGID$symbol <- rownames(EGID)
colnames(EGID)[1] <- "EntrezID"
gene_summ <- getGenes(as.numeric(as.character(EGID$EntrezID)), fields="summary")
EGID$summary <- gene_summ$summary
View(EGID)

```

##Visualise cliques
```{r}
## Jaccard similarity function
library(arrangements)
library(ggdendro)
library(ggplot2)
make_matrix <- function(cliq_list) {
  
 # comb <- combinations(names(cliq_list), 2, replace = F)
 comb <- combinations(names(cliq_list), 2, replace = T) #include diagonals
  prct <- list()
  a_len <- list()
  b_len <- list()
  a_len_ov <- list()
  b_len_ov <- list()
  ov_tot <- list()
  for (i in 1:nrow(comb)) {
  #  a <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 1],]$mods), ","))
  #  b <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 2],]$mods), ","))
    a <- cliq_list[[comb[i,1]]]
    b <- cliq_list[[comb[i,2]]]
    prct[[i]] <- 2 * length(intersect(a, b)) / (length(a) + length(b))
    a_len[[i]] <- length(a) 
    b_len[[i]] <- length(b)
    a_len_ov[[i]] <- length(a[a %in% b])/length(a)
    b_len_ov[[i]] <- length(b[b %in% a])/length(b)
    ov_tot[[i]] <- length(intersect(a, b))
    # cat("\nMatching between", comb[i, 1], "and", comb[i, 2], "is", prct)
  }
  
  comb1 <- cbind.data.frame(comb, "perc" = unlist(prct), "c1" = unlist(a_len), "c2" = unlist(b_len),
                            "c1_perc_ov" = unlist(a_len_ov), "c2_perc_ov" = unlist(b_len_ov), 
                            "ov_tot" = unlist(ov_tot), stringsAsFactors=FALSE)
  colnames(comb1)[1] <- "m1"
  colnames(comb1)[2] <- "m2"
  
  return(comb1)
 
}
te3_list <- lapply(te3, function(x)names(x))
cliq_jacc_sim <- make_matrix(te3)
#library(reshape2)
#raw_mat <- acast(cliq_jacc_sim, m1 ~ m2, value.var="ov_tot")

g <- graph.data.frame(cliq_jacc_sim[,c(1:3)], directed=FALSE)
raw_mat <- get.adjacency(g, attr="perc", sparse=FALSE)
##function to extract cluster after specifying a cutpoint
cluster_mem <- function(mat_inp){
hc <- hclust(dist(mat_inp), "ave")
#plot(hc, hang = -1, cex = 0.8)
#abline(h = 1.5, lty = 2)
#groups <- cutree(hc, h=1.5)

#cliq_clusters <- cbind("cliq_name"= rownames(raw_mat),groups)

###start here
groups <- cutree(hc, h=1)
plot(hc, hang = -1, cex = 0.8)
gg <- rect.hclust(hc,k=length(unique(groups)))
return(gg)
}
gg1 <- cluster_mem(raw_mat)
hc <- hclust(dist(raw_mat), "ave")
groups <- cutree(hc, h=1)
clust.gr<-data.frame(num=unlist(gg1), clust=rep(c(paste0("Clust_",1:length(unique(groups)))),times=sapply(gg1,length)))
dendr <- dendro_data(hc, type="rectangle") 
text.df<-merge(label(dendr),clust.gr,by.x="label",by.y="row.names")
ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=text.df, aes(x=x, y=y, label=label, hjust=0,color=clust), size=3) +
  geom_hline(yintercept=1, linetype="dashed") + 
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

```

##Some notes: GRIA2, KIF complex, SEC24B seem to be directly implicated in neuronal diseases (Peho syndrome)
##Singh et. al (SCHEMA consortium) https://www.medrxiv.org/content/10.1101/2020.09.18.20192815v1.full.pdf; identifies 10 genes from exome wide RVAS
##case = 24248, control: 97322
##The annotated functions of these genes are diverse and include ion transport (CACNA1G, GRIN2A, and GRIA3), neuronal migration and growth (TRIO), transcriptional regulation (SP4, RB1CC1, and SETD1A), nuclear transport (XPO7), and ubiquitin ligation (CUL1, HERC1).
#table(group_tab$genes %in% c("CACNA1G", "GRIN2A", "GRIA3", "SP4", "RB1CC1", "SETD1A", "TRIO", "XPO7", "CUL1", "HERC1")) ##none were found in the top 100 genes in ASRB

##Alternate plotting

```{r}
#https://cran.r-project.org/web/packages/dendextend/vignettes/dendextend.html
#dend <- raw_mat %>%  scale %>% 
#        dist %>% hclust %>% as.dendrogram
#Already scaled as the Jaccard Index is expressed as percentages

dend <- raw_mat %>% dist %>% hclust %>% as.dendrogram
dend %>% plot
lab_ord <- labels(dend)
cust_col_df <- cbind.data.frame("code" = paste("Clust", 1:7, sep = "_"), "col_cust" = c("#008fd5","#de6b35", "#7a9406", "#fc0373","#8f5467", "#6c0ee8", "#03fcca"))
text.df$col_cust <- as.character(cust_col_df[match(as.character(text.df$clust), cust_col_df$code), 2])
text.df <- text.df[match(lab_ord, as.character(text.df$label)),]
#write.table(text.df, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/node_cluster_color_map.tsv", sep = "\t", row.names = F, quote = F)
#dend %>% set("labels_col", text.df$col_cust) %>% plot
#abline(v = 1.5, lty = 2)
##use this
dend1 <- dend %>% set("branches_k_color", text.df$col_cust) %>% set("branches_lwd", 1.2) %>%
   set("labels_colors", text.df$col_cust) %>% set("labels_cex", 0.8)
ggd1 <- as.ggdend(dend1)
ggplot(ggd1, horiz = TRUE, theme = NULL) + geom_hline(yintercept=1.0, linetype="dashed") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

##Circular dendrogram
# ggplot(ggd1, labels = FALSE) + 
#   scale_y_reverse(expand = c(0.2, 0)) +
#   coord_polar(theta="x")

library(circlize)

dend2 <- dend1 %>% set("branches_lwd", c(5,5,5,5,5,5,5))
circlize_dendrogram(dend2, labels = T)

```


##Collapse cliques

```{r}
strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")
collapsed_cliques <- lapply(gg1, function(x)unique(unlist(lapply(te3[names(x)], function(y)names(y)))))
names(collapsed_cliques) <- paste("Clust", 1:length(collapsed_cliques), sep = "_")
saveRDS(collapsed_cliques,"~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Cliques/collapsed_cliques_ASRB.rds", compress = T)
#text.df
cust_col_df <- cbind.data.frame("code" = paste("Clust", 1:7, sep = "_"), "col_cust" = c("#008fd5","#de6b35", "#7a9406", "#fc0373","#8f5467", "#6c0ee8", "#03fcca"))
text.df$col_cust <- as.character(cust_col_df[match(as.character(text.df$clust), cust_col_df$code), 2])
#text.df <- text.df[match(lab_ord, as.character(text.df$label)),]

plot_col_cliq <- function(col_cliq_df, clust_id){
 # cpx_genes <- names(cliq_list)
  col <- unique(as.character(col_cliq_df[as.character(col_cliq_df$clust) %in% clust_id,6]))
  print(col)
  cliq_mem <- unlist(collapsed_cliques[clust_id])
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cliq_mem 
                                 & as.character(can_net1$to) %in% cliq_mem, ])
  
  cpx_graph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
  net_new_t_list <- network(net_mat_t_list, directed = FALSE)
  network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
  
  cpx_plt <- ggnet2(net_new_t_list, alpha = 0.75, node.size = 4, edge.alpha = 0.5, label = TRUE, label.size = 2.5, edge.color = col,  mode = "kamadakawai")
  cpx_plt <- cpx_plt + scale_color_manual(values = col)
return(cpx_plt)
}

cliq_col_list <- list()
for(k in 1:length(collapsed_cliques)){
  cliq_col_list[[k]] <- plot_col_cliq(text.df, paste("Clust", k, sep = "_"))
}

source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
#multiplot(plotlist = cliq_col_list, cols = 3)
multiplot(cliq_col_list[[7]],
  cliq_col_list[[6]], 
          cliq_col_list[[5]],
          cliq_col_list[[4]],
          cliq_col_list[[3]],
          cliq_col_list[[1]],
          cliq_col_list[[2]],
          cols = 2)

```

##make sif files from collapsed cliques for cytoscape
```{r}
make_sif_cliq <- function(col_cliq_list){
 # cpx_genes <- names(cliq_list)
  #col <- unique(as.character(col_cliq_df[as.character(col_cliq_df$clust) %in% clust_id,6]))
  #print(col)
  
  cliq_mem <- unlist(col_cliq_list)
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cliq_mem 
                                 & as.character(can_net1$to) %in% cliq_mem, ])
  prot_np_all$interaction <- "combined_score"
  prot_np_all$combined_score <- 1
  colnames(prot_np_all)[1:2] <- c("node1", "node2")
  prot_np_all_sif <- prot_np_all[,c(1,3,2,4)]
  return(prot_np_all_sif)
}
sif_list <- lapply(collapsed_cliques, function(x)make_sif_cliq(x))
sif_list_comb <- do.call("rbind.data.frame", sif_list)
write.table(sif_list_comb,"~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Cliques/Collapse_cliques.sif", sep = " ", row.names = F, quote = F)

color_map_prot <- mapply(cbind, collapsed_cliques, "SampleID"=names(collapsed_cliques), SIMPLIFY=F)
color_map_prot_df <- do.call("rbind.data.frame", color_map_prot)
color_map_prot_df$SampleID <- as.numeric(gsub("Clust_", "", color_map_prot_df$SampleID))
colnames(color_map_prot_df) <- c("node1", "col_name")
write.table(color_map_prot_df,"~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Cliques/Colormap_cliques.tsv", sep = "\t", row.names = F, quote = F)
```

##Clique significance (Fisher's test)
```{r}
#####################################
##Burden test
cpx_OR_fisher <- function(ppi_res,cliq_list, case_coh_size, cont_coh_size, coh){
  ft_df <- list()
  for(i in 1:length(cliq_list)){
    print(i)
    ppi_res_tab <- ppi_res[ppi_res$gene %in% cliq_list[[i]],]
    # ppi_res_tab[,2] <- ifelse(ppi_res_tab[,2] == 0, 1, ppi_res_tab[,2])
    inp <- c(sum(ppi_res_tab[,1]), case_coh_size - sum(ppi_res_tab[,1]) , 
             sum(ppi_res_tab[,2]), cont_coh_size - sum(ppi_res_tab[,2]))
    sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
    colnames(sim_mat) <- c("case", "cont")
    rownames(sim_mat) <- c("hits", "no_hits")
    #ft <- fisher.test(sim_mat, alternative = "greater")
    #ft <- fisher.test(sim_mat)
    ft <- fisher.test(sim_mat, conf.int = T, conf.level = 0.99)
    ft_df[[i]] <- cbind.data.frame("clique" = names(cliq_list)[i] ,"Cases" = sum(ppi_res_tab[,1]),
                                   "Controls" = sum(ppi_res_tab[,2]),
                                   "Fish_pval" = ft$p.value,"CI_lower" = ft$conf.int[1],
                                   "CI_upper" = ft$conf.int[2],
                                   "OR_Fish" = ft$estimate, "case_coh_size" = case_coh_size,
                                   "Coh" = coh, "genes" = paste(names(cliq_list[[i]]), collapse = ","))
  }
  return(ft_df)
}
collapsed_cliques <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/CAIRNS/round2/ASRB_AR_AD/SKAT/Cliques/collapsed_cliques_ASRB.rds")

##ASRB vs MGRB enrichment
asrb_mgrb_genes <- Exome_pc123_srt_SKAT_case_enr_nCH[[4]]

cpx_ASRB_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(asrb_mgrb_genes, collapsed_cliques, 406, 3205, "ASRBvsMGRB"))
cpx_ASRB_OR_df$adj_pval <- p.adjust(cpx_ASRB_OR_df$Fish_pval, method = "bonferroni", n = length(cpx_ASRB_OR_df$Fish_pval))

##ISKS vs MGRB enrichment
isks_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/Exome_para_tab_ISKS_MGRB_C345_Aug31.rds")

cpx_ISKS_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes, collapsed_cliques, 1644, 3205, "ISKSvsMGRB"))
cpx_ISKS_OR_df$adj_pval <- p.adjust(cpx_ISKS_OR_df$Fish_pval, method = "bonferroni", n = length(cpx_ISKS_OR_df$Fish_pval))


```


