---
title: "visualization_summary"
author: "Swetansu Pattnaik"
date: "07/10/2020"
output: html_document
---

```{r setup, include=FALSE}
#.libPaths(c( "/home/shu/R/x86_64-redhat-linux-gnu-library/3.4", .libPaths() ) )
`%nin%` = Negate(`%in%`)
knitr::opts_chunk$set(echo = TRUE)
```

##load libraries
```{r echo = FALSE, warning = FALSE, message = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}
library(readxl)
library(ggplot2)
library(ggdendro)
library(dendextend)
library(dplyr)
library(ggrepel)
library(knitr)
library(igraph)
library(ggnet)
library(intergraph)
library(network)
library(org.Hs.eg.db)
library(topGO)
```


##Clique detection and significance
```{r}
##refer script (cliq_OR_SKAT.R)

#cpx_list <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/Cliques_max101.rds")
cpx_list <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/review_doc/Cliques/Cliques_max64_PC1_sub.rds")

cpx_genes <- unique(unlist(lapply(cpx_list, function(x)names(x))))
##filter list based on burden test (adjusted Pval < 0.01)
comb_burd_SKAT <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/review_doc/Cliques/Clique_OR_SKAT_PC1_sub.tsv", sep = "\t", header = T, stringsAsFactors = F)
sig_cliq <- comb_burd_SKAT[comb_burd_SKAT$adj_pval < 0.01,]$clique
sig_cliq_df <- comb_burd_SKAT[comb_burd_SKAT$adj_pval < 0.01,]
sig_cliq_df$size <- unlist(lapply(strsplit(sig_cliq_df$genes, ","), function(x)length(x)))

cpx_list_filt <- cpx_list[sig_cliq]
cpx_genes_filt <- unique(unlist(lapply(cpx_list_filt, function(x)names(x))))

##plot p-values
sig_cliq_df_sub <- sig_cliq_df[,c(11:12,15)]
sig_cliq_df_sub <- sig_cliq_df_sub[order(sig_cliq_df_sub$adj_pval, decreasing = F),]
sig_cliq_df_sub$eg_ID <- factor(sig_cliq_df_sub$eg_ID, levels = sig_cliq_df_sub$eg_ID[order(sig_cliq_df_sub$adj_pval)])
sig_cliq_df_sub$size <- as.factor(sig_cliq_df_sub$size)
#melted_sig_cliq <- melt(sig_cliq_df_sub) ##pairwise bar plot of SKAT and burden test pvalues

# p2 <- ggplot(data=melted_sig_cliq, aes(x=eg_ID, y=-log10(value), fill=variable)) +
# geom_bar(stat="identity", position=position_dodge())
# p2 + theme(axis.text.x = element_text(angle = 45))

p3 <- ggplot(data=sig_cliq_df_sub, aes(x=eg_ID, y=-log10(adj_pval), fill=size)) +
geom_bar(stat="identity", position=position_dodge()) + theme_minimal()
p3 + theme(axis.text.x = element_text(angle = 45)) + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#4032A8", "#9c9014")) 

##cliques of size greater than 4

# sig_cliq_df_sub_gt4 <- sig_cliq_df_sub[as.numeric(as.character(sig_cliq_df_sub$size)) > 4, ]
# p4 <- ggplot(data=sig_cliq_df_sub_gt4, aes(x=eg_ID, y=-log10(adj_pval), fill=size)) +
# geom_bar(stat="identity", position=position_dodge()) + theme_minimal()
# p4 + theme(axis.text.x = element_text(angle = 45)) + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#4032A8", "#9c9014"))

```


##cliques of interest(redundant chunk)
```{r}

strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")

plot_func_cliq <- function(cliq_list){
  cpx_genes <- names(cliq_list)
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cpx_genes 
                                 & as.character(can_net1$to) %in% cpx_genes, ])
  
  cpx_graph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
  net_new_t_list <- network(net_mat_t_list, directed = FALSE)
  network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
  
  cpx_plt <- ggnet2(net_new_t_list, alpha = 0.75, node.size = 4, edge.alpha = 0.5, label = TRUE, label.size = 2.5,  mode = "kamadakawai")
return(cpx_plt)
}

#all_cliq_plot <- lapply(cpx_list_filt, function(x)plot_func_cliq(x))
e1 <- plot_func_cliq(cpx_list_filt$c_101)
#plot_func_cliq(cpx_list_filt$c_71)
e2 <- plot_func_cliq(cpx_list_filt$c_88)
e3 <- plot_func_cliq(cpx_list_filt$c_78)
e4 <- plot_func_cliq(cpx_list_filt$c_68)
e5 <- plot_func_cliq(cpx_list_filt$c_34)
##cliques of size greater than 4
#cpx_list_filt_gt4 <- cpx_list_filt[names(cpx_list_filt[which(sapply(cpx_list_filt, function(x)length(x) > 4))])]
source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
multiplot(e1,e2,e3,e4,e5, cols = 2)
multiplot(e1,e2,e3,e5, cols = 2)

```


```{r}
#source("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/git_proj_rvas/Comb_set_round2/ISKS_MGRB_2020/ISKS_AR_AD/Aug31_freeze/Cliq_analysis/Cliq_collapse.R")
```


##hierarchical clustering of cliques based on similarity
```{r}

## Jaccard similarity function
library(arrangements)
library(ggdendro)
library(ggplot2)
make_matrix <- function(cliq_list) {
  
 # comb <- combinations(names(cliq_list), 2, replace = F)
 comb <- combinations(names(cliq_list), 2, replace = T) #include diagonals
  prct <- list()
  a_len <- list()
  b_len <- list()
  a_len_ov <- list()
  b_len_ov <- list()
  ov_tot <- list()
  for (i in 1:nrow(comb)) {
  #  a <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 1],]$mods), ","))
  #  b <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 2],]$mods), ","))
    a <- cliq_list[[comb[i,1]]]
    b <- cliq_list[[comb[i,2]]]
    prct[[i]] <- 2 * length(intersect(a, b)) / (length(a) + length(b))
    a_len[[i]] <- length(a) 
    b_len[[i]] <- length(b)
    a_len_ov[[i]] <- length(a[a %in% b])/length(a)
    b_len_ov[[i]] <- length(b[b %in% a])/length(b)
    ov_tot[[i]] <- length(intersect(a, b))
    # cat("\nMatching between", comb[i, 1], "and", comb[i, 2], "is", prct)
  }
  
  comb1 <- cbind.data.frame(comb, "perc" = unlist(prct), "c1" = unlist(a_len), "c2" = unlist(b_len),
                            "c1_perc_ov" = unlist(a_len_ov), "c2_perc_ov" = unlist(b_len_ov), 
                            "ov_tot" = unlist(ov_tot), stringsAsFactors=FALSE)
  colnames(comb1)[1] <- "m1"
  colnames(comb1)[2] <- "m2"
  
  return(comb1)
 
}

cliq_jacc_sim <- make_matrix(cpx_list_filt)
#library(reshape2)
#raw_mat <- acast(cliq_jacc_sim, m1 ~ m2, value.var="ov_tot")

g <- graph.data.frame(cliq_jacc_sim[,c(1:3)], directed=FALSE)
raw_mat <- get.adjacency(g, attr="perc", sparse=FALSE)
##function to extract cluster after specifying a cutpoint
cluster_mem <- function(mat_inp){
hc <- hclust(dist(mat_inp), "ave")
#plot(hc, hang = -1, cex = 0.8)
#abline(h = 1.5, lty = 2)
groups <- cutree(hc, h=1.5)

#cliq_clusters <- cbind("cliq_name"= rownames(raw_mat),groups)

###start here
groups <- cutree(hc, h=1.5)
plot(hc, hang = -1, cex = 0.8)
gg <- rect.hclust(hc,k=length(unique(groups)))
return(gg)
}
gg1 <- cluster_mem(raw_mat)
hc <- hclust(dist(raw_mat), "ave")
groups <- cutree(hc, h=1.5)
clust.gr<-data.frame(num=unlist(gg1), clust=rep(c(paste0("Clust_",1:length(unique(groups)))),times=sapply(gg1,length)))
dendr <- dendro_data(hc, type="rectangle") 
text.df<-merge(label(dendr),clust.gr,by.x="label",by.y="row.names")

ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=text.df, aes(x=x, y=y, label=label, hjust=0,color=clust), size=3) +
  geom_hline(yintercept=1.5, linetype="dashed") + 
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())



```


##Alternate plotting

```{r}
#dend <- raw_mat %>%  scale %>% 
#        dist %>% hclust %>% as.dendrogram
#Already scaled as the Jaccard Index is expressed as percentages
dend <- raw_mat %>% dist %>% hclust %>% as.dendrogram
dend %>% plot
lab_ord <- labels(dend)
cust_col_df <- cbind.data.frame("code" = paste("Clust", 1:8, sep = "_"), "col_cust" = c("#008fd5","#de6b35", "#7a9406", "#fc0373","#8f5467", "#6c0ee8", "#FF3333", "#AFFF33"))
text.df$col_cust <- as.character(cust_col_df[match(as.character(text.df$clust), cust_col_df$code), 2])
text.df <- text.df[match(lab_ord, as.character(text.df$label)),]
#write.table(text.df, "~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/node_cluster_color_map.tsv", sep = "\t", row.names = F, quote = F)
#dend %>% set("labels_col", text.df$col_cust) %>% plot
#abline(v = 1.5, lty = 2)
##use this
dend1 <- dend %>% set("branches_k_color", text.df$col_cust) %>% set("branches_lwd", 1.2) %>%
   set("labels_colors", text.df$col_cust) %>% set("labels_cex", 0.8)
ggd1 <- as.ggdend(dend1)
ggplot(ggd1, horiz = TRUE, theme = NULL) + geom_hline(yintercept=1.5, linetype="dashed") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

##Circular dendrogram
ggplot(ggd1, labels = FALSE) + 
  scale_y_reverse(expand = c(0.2, 0)) +
  coord_polar(theta="x")

```

##Clique collapse based on clustering and adding color
```{r warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}

strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")
collapsed_cliques <- lapply(gg1, function(x)unique(unlist(lapply(cpx_list_filt[names(x)], function(y)names(y)))))
names(collapsed_cliques) <- paste("Clust", 1:8, sep = "_")
#text.df
plot_col_cliq <- function(col_cliq_df, clust_id){
 # cpx_genes <- names(cliq_list)
  col <- unique(as.character(col_cliq_df[as.character(col_cliq_df$clust) %in% clust_id,6]))
  print(col)
  cliq_mem <- unlist(collapsed_cliques[clust_id])
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cliq_mem 
                                 & as.character(can_net1$to) %in% cliq_mem, ])
  
  cpx_graph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
  net_new_t_list <- network(net_mat_t_list, directed = FALSE)
  network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
  
  cpx_plt <- ggnet2(net_new_t_list, alpha = 0.75, node.size = 4, edge.alpha = 0.5, label = TRUE, label.size = 2.5, edge.color = col,  mode = "kamadakawai")
  cpx_plt <- cpx_plt + scale_color_manual(values = col)
return(cpx_plt)
}

cliq_col_list <- list()
for(k in 1:8){
  cliq_col_list[[k]] <- plot_col_cliq(text.df, paste("Clust", k, sep = "_"))
}

source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
#multiplot(plotlist = cliq_col_list, cols = 3)
multiplot(cliq_col_list[[6]], 
          cliq_col_list[[5]],
          cliq_col_list[[4]],
          cliq_col_list[[3]],
          cliq_col_list[[1]],
          cliq_col_list[[2]],
          cliq_col_list[[7]],
          cliq_col_list[[8]],
          cols = 2)
```


##Burden test 
```{r warning = FALSE, figure.align = "center", figure.height = 10, figure.width = 12}

cpx_OR_fisher <- function(ppi_res,case_coh_size, cont_coh_size, coh){
  ft_df <- list()
  for(i in 1:length(collapsed_cliques)){
    ppi_res_tab <- ppi_res[ppi_res$gene %in% collapsed_cliques[[i]],]
   # ppi_res_tab[,2] <- ifelse(ppi_res_tab[,2] == 0, 1, ppi_res_tab[,2])
    inp <- c(sum(ppi_res_tab[,1]), case_coh_size - sum(ppi_res_tab[,1]) , 
             sum(ppi_res_tab[,2]), cont_coh_size - sum(ppi_res_tab[,2]))
    sim_mat <- matrix(inp ,nrow = 2, ncol = 2)
    colnames(sim_mat) <- c("case", "cont")
    rownames(sim_mat) <- c("hits", "no_hits")
    #ft <- fisher.test(sim_mat, alternative = "greater")
    #ft <- fisher.test(sim_mat)
    ft <- fisher.test(sim_mat, conf.int = T, conf.level = 0.99)
    ft_df[[i]] <- cbind.data.frame("gene" = names(collapsed_cliques)[i] ,"Cases" = sum(ppi_res_tab[,1]), "Controls" = sum(ppi_res_tab[,2]),
                                   "Fish_pval" = ft$p.value,"CI_lower" = ft$conf.int[1],
                                   "CI_upper" = ft$conf.int[2],
                                   "OR_Fish" = ft$estimate, "case_coh_size" = case_coh_size,
                                     "Coh" = coh)
  }
  return(ft_df)
}

##get frequency tables
isks_mgrb_genes <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/Exome_para_tab_ISKS_MGRB_C345_Aug31.rds")
isks_mgrb_genes_noC3 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Exome_para_tab_ISKS_MGRB_minusC3_Aug31.rds")

##burden test
cpx_ISKS_OR_df <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes, 1644, 3205, "ISKS_C345"))
cpx_ISKS_OR_df_noC3 <- do.call("rbind.data.frame", cpx_OR_fisher(isks_mgrb_genes_noC3, 1644, 3205, "ISKS_C45"))
comb_df_C45_C3 <- rbind.data.frame(cpx_ISKS_OR_df, cpx_ISKS_OR_df_noC3)
comb_df_C45_C3$col <- text.df[match(comb_df_C45_C3$gene,text.df$clust),6]
  
forest_custplot <- function(df, repset = NULL){
#  dotCOLS = c("#a6d8f0","#f9b282", "#78f542", "#f5c6e5", "#ffe3bf", "#cfabff")
#  barCOLS = c("#008fd5","#de6b35", "#7a9406", "#fc0373", "#f79514", "#6c0ee8")
  df$Coh <- droplevels(df$Coh)
  ##with replication set (combined sarcomas)
  if(repset == 1){
 # dotCOLS = c("#a6d8f0","#f9b282", "#78f542", "#f5c6e5","#cfabff", "#232533", "#bdb071", "#f52a6b", "#2a7ff5")
#  barCOLS = c("#008fd5","#de6b35", "#7a9406", "#fc0373","#6c0ee8", "#a3ceff", "#717bbd", "#8f5467", "#f5822a")
    
  dotCOLS = c("Red", "Blue")
  barCOLS = rep("#232533", length(dotCOLS))
  
  }
  else{
    df <- df[df$Coh %nin% "REP",]
    ##without Cairns
  #  dotCOLS = c("#a6d8f0","#f9b282", "#78f542", "#f5c6e5","#cfabff")
  #  barCOLS = c("#008fd5","#de6b35", "#7a9406", "#fc0373","#6c0ee8")
    dotCOLS = c("Red", "Blue")
  barCOLS = rep("#232533", length(dotCOLS))
  }
  p <- ggplot(df, aes(x=gene, y=log(OR_Fish), ymin=log(CI_lower), ymax=log(CI_upper),col=Coh,fill=Coh)) + 
    #specify position here
    geom_linerange(size=1,position=position_dodge(width = 0.5)) +
    geom_hline(yintercept=0, lty=2) +
  #  geom_hline(yintercept=1, lty=2) +
    #specify position here too
    geom_point(size=5, shape=21, colour="white", stroke = 0.5,position=position_dodge(width = 0.5)) +
    scale_fill_manual(values=dotCOLS)+
    scale_color_manual(values=barCOLS)+
    scale_x_discrete(name="Protein modules") + 
    scale_y_continuous(name="Log Odds ratio") +
    coord_flip() +
    theme_minimal() + theme(legend.position="bottom") + theme(legend.title = element_blank()) +
    theme(legend.text = element_text(size=8)) + theme(axis.text.y = element_text(hjust = 1, colour = unique(comb_df_C45_C3$col)))
  return(p)
}

p_isks <- forest_custplot(comb_df_C45_C3, repset = 1) + ggtitle("Clustered Cliques") + guides(fill=guide_legend(nrow=2,byrow=TRUE)) + theme(legend.position="right")

p_isks

#devtools::install_github("haozhu233/kableExtra")
#library(kableExtra)
df_tab <- comb_df_C45_C3[,c(1:7,9)]
rownames(df_tab) <- NULL
kable(df_tab, caption = "Final Cliques")

```


##make sif files from collapsed cliques for cytoscape
```{r}
make_sif_cliq <- function(col_cliq_list){
 # cpx_genes <- names(cliq_list)
  #col <- unique(as.character(col_cliq_df[as.character(col_cliq_df$clust) %in% clust_id,6]))
  #print(col)
  
  cliq_mem <- unlist(col_cliq_list)
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cliq_mem 
                                 & as.character(can_net1$to) %in% cliq_mem, ])
  prot_np_all$interaction <- "combined_score"
  prot_np_all$combined_score <- 1
  colnames(prot_np_all)[1:2] <- c("node1", "node2")
  prot_np_all_sif <- prot_np_all[,c(1,3,2,4)]
  return(prot_np_all_sif)
}
sif_list <- lapply(collapsed_cliques, function(x)make_sif_cliq(x))
sif_list_comb <- do.call("rbind.data.frame", sif_list)
write.table(sif_list_comb,"~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/Collapse_cliques.sif", sep = " ", row.names = F, quote = F)

color_map_prot <- mapply(cbind, collapsed_cliques, "SampleID"=names(collapsed_cliques), SIMPLIFY=F)
color_map_prot_df <- do.call("rbind.data.frame", color_map_prot)
color_map_prot_df$SampleID <- as.numeric(gsub("Clust_", "", color_map_prot_df$SampleID))
colnames(color_map_prot_df) <- c("node1", "col_name")
write.table(color_map_prot_df,"~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Aug31/Cliques/Colormap_cliques.tsv", sep = "\t", row.names = F, quote = F)
```


##Clique collapse based on clustering

```{r}

collapsed_cliques <- lapply(gg1, function(x)unique(unlist(lapply(cpx_list_filt[names(x)], function(y)names(y)))))
names(collapsed_cliques)
strindb_biog_graph1 <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/SKAT/strindb_biog_graph_cyto.rds")

plot_collap_cliq <- function(cliq_mem){
 # cpx_genes <- names(cliq_list)
  can_net1 <- igraph::as_data_frame(strindb_biog_graph1, what = "edges")
  prot_np_all <- unique(can_net1[as.character(can_net1$from) %in% cliq_mem 
                                 & as.character(can_net1$to) %in% cliq_mem, ])
  
  cpx_graph <- igraph::graph.data.frame(prot_np_all, directed = F)
  
  net_mat_t_list <- get.adjacency(cpx_graph, type=c("both"), attr=NULL, names=TRUE, sparse = FALSE)
  net_new_t_list <- network(net_mat_t_list, directed = FALSE)
  network.vertex.names(net_new_t_list) <- V(cpx_graph)$name
  
  cpx_plt <- ggnet2(net_new_t_list, alpha = 0.75, node.size = 4, edge.alpha = 0.5, label = TRUE, label.size = 2.5,  mode = "kamadakawai")
return(cpx_plt)
}


cliq_plots <- lapply(collapsed_cliques, function(x)plot_collap_cliq(x))
source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
multiplot(plotlist = cliq_plots, cols = 2)
```

##FAST GENE SET ENRICHMENT ANALYSIS (fgsea) for unbiased estimates of clique significance
##Also performs leading edge analysis to identify drivers in a geneset

```{r}
`%nin%` = Negate(`%in%`)
Exome_skat <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/review_doc/SKAT/Exome_skat_para_result_isks_totex_count_PC1234_ver4_clinrect_Aug31_subPC1.rds")
df_skat <- lapply(Exome_skat, function(x)do.call("rbind.data.frame", x))
Exome_pc123_srt_SKAT <- lapply(df_skat, function(x) x[order(x$pval_SKATbin, decreasing = F),])
Exome_pc123_srt_SKAT <- lapply(Exome_pc123_srt_SKAT, function(x){colnames(x)[1] <- c("symbol"); return(x)})
Exome_pc123_srt_SKAT_case_enr_nCH_df <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/Exome_para_tab_ISKS_MGRB_C345_Aug31_sub_PC1.rds")
Exome_pc123_srt_SKAT_df <- Exome_pc123_srt_SKAT[[4]]

Exome_pc123_srt_SKAT_df =  Exome_pc123_srt_SKAT_df[Exome_pc123_srt_SKAT_df$symbol %in% Exome_pc123_srt_SKAT_case_enr_nCH_df$gene,]

Exome_pc123_srt_SKAT_case_enr_nCH_df <- Exome_pc123_srt_SKAT_case_enr_nCH_df[Exome_pc123_srt_SKAT_case_enr_nCH_df$gene %in% Exome_pc123_srt_SKAT_df$symbol,]

##Add p-value
#Exome_pc123_srt_SKAT_case_enr_nCH_pval <- Map(cbind.data.frame, Exome_pc123_srt_SKAT_case_enr_nCH, Exome_pc123_srt_SKAT)
Exome_pc123_srt_SKAT_case_enr_nCH_df_srt <- Exome_pc123_srt_SKAT_case_enr_nCH_df[match(as.character(Exome_pc123_srt_SKAT_df$symbol),as.character(Exome_pc123_srt_SKAT_case_enr_nCH_df$gene)),]

Exome_pc123_srt_SKAT_case_enr_nCH_pval <- cbind.data.frame(Exome_pc123_srt_SKAT_case_enr_nCH_df_srt,Exome_pc123_srt_SKAT_df)


##compute rank score
Exome_pc123_srt_SKAT_case_enr_nCH_pval$rank_score <- -log10(Exome_pc123_srt_SKAT_case_enr_nCH_pval$pval_SKATbin) * Exome_pc123_srt_SKAT_case_enr_nCH_pval$wt_diff
##sort to generate ranked list                                                    
Exome_pc123_srt_SKAT_case_enr_nCH_ranked_all <- Exome_pc123_srt_SKAT_case_enr_nCH_pval[order(Exome_pc123_srt_SKAT_case_enr_nCH_pval$rank_score, decreasing = T),]
ranked_list = Exome_pc123_srt_SKAT_case_enr_nCH_ranked_all$rank_score
names(ranked_list) = Exome_pc123_srt_SKAT_case_enr_nCH_ranked_all$gene

##Cliques/Genesets
library(igraph)
library(fgsea)
#data(examplePathways)
#data(exampleRanks)
cpx_list <- readRDS("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/review_doc/Cliques/Cliques_max64_PC1_sub.rds")

comb_burd_SKAT <- read.delim("~/RVAS/shard_sub_tier3/DT_sheet/EXOME_isks_risc/test/comb_set_2020/ISKS_AR_AD/review_doc/Cliques/Clique_OR_SKAT_PC1_sub.tsv", sep = "\t", header = T, stringsAsFactors = F)

sig_cliq <- comb_burd_SKAT[comb_burd_SKAT$adj_pval < 0.01,]$clique

cpx_list <- cpx_list[sig_cliq]
cpx_list <- lapply(cpx_list, function(x)names(x))

##merge cliques
##obtained from script: cliques_for_paper.Rmd (lines 119-178)

## Jaccard similarity function
library(arrangements)
library(ggdendro)
library(ggplot2)
make_matrix <- function(cliq_list) {
  
  # comb <- combinations(names(cliq_list), 2, replace = F)
  comb <- combinations(names(cliq_list), 2, replace = T) #include diagonals
  prct <- list()
  a_len <- list()
  b_len <- list()
  a_len_ov <- list()
  b_len_ov <- list()
  ov_tot <- list()
  for (i in 1:nrow(comb)) {
    #  a <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 1],]$mods), ","))
    #  b <- unlist(strsplit(as.character(exemp_df_L1[exemp_df_L1$L1 == comb[i, 2],]$mods), ","))
    a <- cliq_list[[comb[i,1]]]
    b <- cliq_list[[comb[i,2]]]
    prct[[i]] <- 2 * length(intersect(a, b)) / (length(a) + length(b))
    a_len[[i]] <- length(a) 
    b_len[[i]] <- length(b)
    a_len_ov[[i]] <- length(a[a %in% b])/length(a)
    b_len_ov[[i]] <- length(b[b %in% a])/length(b)
    ov_tot[[i]] <- length(intersect(a, b))
    # cat("\nMatching between", comb[i, 1], "and", comb[i, 2], "is", prct)
  }
  
  comb1 <- cbind.data.frame(comb, "perc" = unlist(prct), "c1" = unlist(a_len), "c2" = unlist(b_len),
                            "c1_perc_ov" = unlist(a_len_ov), "c2_perc_ov" = unlist(b_len_ov), 
                            "ov_tot" = unlist(ov_tot), stringsAsFactors=FALSE)
  colnames(comb1)[1] <- "m1"
  colnames(comb1)[2] <- "m2"
  
  return(comb1)
  
}

cliq_jacc_sim <- make_matrix(cpx_list)
#library(reshape2)
#raw_mat <- acast(cliq_jacc_sim, m1 ~ m2, value.var="ov_tot")

g <- graph.data.frame(cliq_jacc_sim[,c(1:3)], directed=FALSE)
raw_mat <- get.adjacency(g, attr="perc", sparse=FALSE)
##function to extract cluster after specifying a cutpoint
##cutpoint determined by plotting the hc object
cluster_mem <- function(mat_inp){
  hc <- hclust(dist(mat_inp), "ave")
  ###start here
  groups <- cutree(hc, h=1.5)
  plot(hc, hang = -1, cex = 0.8)
  gg <- rect.hclust(hc,k=length(unique(groups)))
  return(gg)
}
gg1 <- cluster_mem(raw_mat)

collapsed_cliques <- lapply(gg1, function(x)unique(unlist(lapply(cpx_list[x], function(y)y))))
collapsed_cliques[[9]] = c("BRCA1", "BRCA2", "PALB2", "ATM", "CHEK2", "CDH1") #negative control
names(collapsed_cliques) <- paste("Clust", 1:9, sep = "_")

##run fgsea
set.seed(4532)
fgseaRes_col <- fgsea(pathways = collapsed_cliques, 
                  stats    = ranked_list,
                  minSize  = 4,
                  maxSize  = 500, nperm = 10000, nproc = 8)
View(fgseaRes_col)
fgseaRes_col$leadingEdge_all = unlist(lapply(fgseaRes_col$leadingEdge, function(x) paste(x, collapse = ",")))
#View(fgseaRes_col[,-8])

```



##GO enrichment of clustered cliques

```{r}
library(enrichR)
dbs <- c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")
clust_GO = lapply(collapsed_cliques, function(x)enrichr(x, dbs))
source("~/APCluster_graphs/case_TCGA_new_PRAD_3431/multi_plot.R")
clust_GO_plots = lapply(clust_GO, function(x)list(plotEnrich(x$GO_Biological_Process_2018), 
                    plotEnrich(x$GO_Molecular_Function_2018), 
                    plotEnrich(x$GO_Cellular_Component_2018)))

multiplot(plotlist = clust_GO_plots[[1]], cols = 3) ##Shelterin
multiplot(plotlist = clust_GO_plots[[4]], cols = 3) ##Centrosome
multiplot(plotlist = clust_GO_plots[[2]], cols = 3)

# pp = plotEnrich(clust_GO[[1]]$GO_Biological_Process_2018)
# plotEnrich(clust_GO[[1]]$GO_Molecular_Function_2018)
# plotEnrich(clust_GO[[1]]$GO_Cellular_Component_2018)
# plotEnrich(clust_GO[[4]]$GO_Biological_Process_2018)
# plotEnrich(clust_GO[[4]]$GO_Molecular_Function_2018)
# plotEnrich(clust_GO[[4]]$GO_Cellular_Component_2018)

```

